---
title: "HOLPA farm-household indicator calculation"
output:
  word_document: default
  pdf_document: default
  html_document: default
date: "2024-12-11"
author: "Sarah Jones (s.jones@cgiar.org)" 
editor_options:
  chunk_output_type: console
---
## Specify settings to use for data analysis

In this section, the user needs to specify which country to analyse, where the cleaned HOLPA survey data are stored on their computer, and any country/landscape specific conversion parameters. This is the only section of the script that needs user input. Subsequent code chunks can be run without making changes.

```{r set user parameters, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)
library(magrittr) # for piping
library(tidyverse) #for formatting data
library(ggplot2) # for plots
library(readr) 
library(reshape2) # for changing data layout
library(stringr) # for wrapping text
library(readxl) # for reading and writing excel files
library(ggsci) # ggplot colours for scientific journals
library(ggforce) # for gauge plots

### Set parameters ####

# Specify country being processed (specify ONE only. You will need to rerun the code to process each country)

#country <- "burkina"
#country <- "india"
#country <- "laos"
#country <- "kenya"
#country <- "peru"
#country <- "senegal" 
#country <- "tunisia"
country <- "zimbabwe"

# for area unit conversions
acre_to_hectare = 0.404686

# replace these file paths with the location where your data are saved:

ref.values.data.path <- "C:/Users/sjones/CGIAR/One CGIAR - Agroecology Initiative Implementation Team - Documents/WP2 Coordination/Task2_Framework/HOLPA implementation/HOLPA_data_use/"

fw_survey_mapping <- read_excel("C:/Users/sjones/CGIAR/One CGIAR - Agroecology Initiative Implementation Team - Documents/WP2 Coordination/Task2_Framework/HOLPA implementation/HOLPA_master/HOLPA_global_field_survey_20231106_mapped_to_indicators.xlsx",sheet="survey")
fw_choices_mapping <- read_excel("C:/Users/sjones/CGIAR/One CGIAR - Agroecology Initiative Implementation Team - Documents/WP2 Coordination/Task2_Framework/HOLPA implementation/HOLPA_master/HOLPA_global_field_survey_20231106_mapped_to_indicators.xlsx",sheet="choices")

global.data.path <- "C:/Users/sjones/OneDrive - CGIAR/Documents/HOLPA/"

bfa.data.path <- "C:/Users/sjones/CGIAR/Sanchez, Andrea Cecilia (Alliance Bioversity-CIAT) - HOLPA_data/Burkina_Faso/burkina_faso_data_clean/bfa/"
ind.data.path <- "C:/Users/sjones/CGIAR/Sanchez, Andrea Cecilia (Alliance Bioversity-CIAT) - HOLPA_data/India/india_data_clean/ind/"
ken.data.path <- "C:/Users/sjones/CGIAR/Sanchez, Andrea Cecilia (Alliance Bioversity-CIAT) - HOLPA_data/Kenya/kenya_data_clean/ken/"
lao.data.path <- "C:/Users/sjones/CGIAR/Sanchez, Andrea Cecilia (Alliance Bioversity-CIAT) - HOLPA_data/Laos/laos_data_clean/lao/"
per.data.path <- "C:/Users/sjones/CGIAR/Sanchez, Andrea Cecilia (Alliance Bioversity-CIAT) - HOLPA_data/Peru/peru_data_clean/per/"
sen.data.path <- "C:/Users/sjones/CGIAR/Sanchez, Andrea Cecilia (Alliance Bioversity-CIAT) - HOLPA_data/Senegal/senegal_data_clean/sen/"
tun.data.path <- "C:/Users/sjones/CGIAR/Sanchez, Andrea Cecilia (Alliance Bioversity-CIAT) - HOLPA_data/Tunisia/tunisia_data_clean/tun/"
zwe.data.path <- "C:/Users/sjones/CGIAR/Sanchez, Andrea Cecilia (Alliance Bioversity-CIAT) - HOLPA_data/Zimbabwe/zimbabwe_data_clean/zwe/"

```

## Import data

Run this chunk to import the relevant HOLPA datasets.

```{r import data,include=FALSE}

#### Import data ####

# reference values for kpi climate mitigation: practice net GHG contributions
ref_values_cc <- read_excel(paste0(ref.values.data.path,"HOLPA data post-processing.xlsx"),sheet="kpi_CC_mitigation")

# reference values for kpi nutrient use: fertilizer unit conversions
ref_values_nut <- read_excel(paste0(ref.values.data.path,"HOLPA data post-processing.xlsx"),sheet="kpi_nutrient_conversion")

# function to import cleaned data

#country_short = "bfa"
#country.data.path = bfa.data.path

import.data <- function(country_short,country.data.path){
  cn <- read_csv(paste0(country.data.path,country_short,"_context_format.csv"),show_col_types = FALSE)
  ae <- read_csv(paste0(country.data.path,country_short,"_agroecology_format.csv"),show_col_types = FALSE)
  ae_scores <- read_csv(paste0(country.data.path,country_short,"_agroecology_score.csv"),show_col_types = FALSE)
  pf <- read_csv(paste0(country.data.path,country_short,"_performance_format.csv"),show_col_types = FALSE)
  fw <- read_csv(paste0(country.data.path,country_short,"_fieldwork_format.csv"),show_col_types = FALSE)

# reshape and classify fieldwork data to enable join with household
  if(!(c("country") %in% colnames(fw))){
    fw <- fw %>% mutate(country = country)
    fw <- melt(fw,id.vars=c("kobo_farmer_id","country"),variable.name="name_question",value.name="name_choice")
  } else{
  fw <- melt(fw[,c(1,2,33:length(fw))],id.vars=c("kobo_farmer_id","country"),variable.name="name_question",value.name="name_choice")}
  
fw <- fw %>% left_join(fw_survey_mapping %>%
                             select(-c("hint::English ((en))" , "appearance",
                                       "relevant" , "constraint" , "choice_filter",
                                       "calculation", "repeat_count",   
                                       "media::image::English ((en))","required")) %>% rename(label_question  = "label::English ((en))"), by=c("name_question"="name_survey"))  %>%
    left_join(fw_choices_mapping %>%
                rename(label_choice  = "label::English ((en))") %>%
                select(c("name_survey" ,"name_choice","label_choice")),
              by=c("name_question"="name_survey","name_choice"="name_choice")) %>%
    filter(!is.na(module)) %>%
  filter(!(subindicator %in% c("respondent_first_name","respondent_last_name"))) %>%
  select(kobo_farmer_id,country,module,theme,indicator,subindicator, fw_site,name_question,label_question, name_choice,label_choice, type) %>% unique()

  image_list <- fw %>% filter(type=="image") %>%
    select(kobo_farmer_id,country,fw_site,name_question,label_question, name_choice)  %>% unique()
  
  country_data <- ae %>% full_join(cn) %>% full_join(pf)  %>% 
    full_join(fw %>% select(-fw_site) %>% unique()) %>%
  full_join(ae_scores) %>% unique() %>% 
    mutate(across(where(is.character),str_trim)) %>% 
    mutate(across(where(is.numeric),str_trim))
  
  assign(paste0(country_short,"_data"),country_data,envir=.GlobalEnv)
  assign(paste0(country_short,"_ae_scores"),ae_scores,envir=.GlobalEnv)
  assign(paste0(country_short,"_cn"),cn,envir=.GlobalEnv)
  assign(paste0(country_short,"_fw"),fw,envir=.GlobalEnv)
  
  if(country == "burkina"){
    write.csv(fw,paste0(bfa.data.path,"bfa_fieldwork_scores.csv"),row.names=FALSE)
    write.csv(image_list,paste0(bfa.data.path,"bfa_fieldwork_photo_list.csv"),row.names=FALSE)}
  
  if(country=="india"){
    write.csv(fw,paste0(ind.data.path,"ind_fieldwork_scores.csv"),row.names=FALSE)
    write.csv(image_list,paste0(ind.data.path,"ind_fieldwork_photo_list.csv"),row.names=FALSE)}
  
  if(country=="laos"){
  write.csv(fw,paste0(lao.data.path,"lao_fieldwork_scores.csv"),row.names=FALSE)
  write.csv(image_list,paste0(lao.data.path,"lao_fieldwork_photo_list.csv"),row.names=FALSE)}
  
  if(country=="kenya"){
    write.csv(fw,paste0(ken.data.path,"ken_fieldwork_scores.csv"),row.names=FALSE)
    write.csv(image_list,paste0(ken.data.path,"ken_fieldwork_photo_list.csv"),row.names=FALSE)}
  
  if(country=="peru"){
  write.csv(fw,paste0(per.data.path,"per_fieldwork_scores.csv"),row.names=FALSE)
  write.csv(image_list,paste0(per.data.path,"per_fieldwork_photo_list.csv"),row.names=FALSE)}
  
  if(country=="senegal"){
  write.csv(fw,paste0(sen.data.path,"sen_fieldwork_scores.csv"),row.names=FALSE)
  write.csv(image_list,paste0(sen.data.path,"sen_fieldwork_photo_list.csv"),row.names=FALSE)}
  
  if(country=="tunisia"){
  write.csv(fw,paste0(tun.data.path,"tun_fieldwork_scores.csv"),row.names=FALSE)
  write.csv(image_list,paste0(tun.data.path,"tun_fieldwork_photo_list.csv"),row.names=FALSE)}
  
  if(country == "zimbabwe"){
  write.csv(fw,paste0(zwe.data.path,"zwe_fieldwork_scores.csv"),row.names=FALSE)
  write.csv(image_list,paste0(zwe.data.path,"zwe_fieldwork_photo_list.csv"),row.names=FALSE)}
}

set_d <- function(country){
  if(country == "burkina"){
  import.data("bfa",bfa.data.path)
  d <- bfa_data
  ref_values_country <- read_excel(paste0(ref.values.data.path,"HOLPA data post-processing.xlsx"),sheet=paste0("BFA","_inputs"))
  iso <- "BFA"
  
  } 
  if(country=="india"){
    import.data("ind",ind.data.path)
    d <- ind_data
    ref_values_country <- read_excel(paste0(ref.values.data.path,"HOLPA data post-processing.xlsx"),sheet=paste0("IND","_inputs"))
    iso <- "IND"
  }
  if(country=="laos"){
      import.data("lao",lao.data.path)
      d <- lao_data
      ref_values_country <- read_excel(paste0(ref.values.data.path,"HOLPA data post-processing.xlsx"),sheet=paste0("LAO","_inputs"))
      iso <- "LAO"
  }
  if(country=="kenya"){
    import.data("ken",ken.data.path)
    d <- ken_data
    ref_values_country <- read_excel(paste0(ref.values.data.path,"HOLPA data post-processing.xlsx"),sheet=paste0("KEN","_inputs"))
    iso <- "KEN"
      }
  if(country=="peru"){
    import.data("per",per.data.path)
    d <- per_data
    ref_values_country <- read_excel(paste0(ref.values.data.path,"HOLPA data post-processing.xlsx"),sheet=paste0("PER","_inputs"))
    iso <- "PER"
  }
  if(country=="senegal"){
    import.data("sen",sen.data.path)
    d <- sen_data
    ref_values_country <- read_excel(paste0(ref.values.data.path,"HOLPA data post-processing.xlsx"),sheet=paste0("SEN","_inputs"))
    iso <- "SEN"
  }
  if(country=="tunisia"){
    import.data("tun",tun.data.path)
    d <- tun_data
    ref_values_country <- read_excel(paste0(ref.values.data.path,"HOLPA data post-processing.xlsx"),sheet=paste0("TUN","_inputs"))
    iso <- "TUN"
  }
  if(country == "zimbabwe"){
    import.data("zwe",zwe.data.path)
    d <- zwe_data
    ref_values_country <- read_excel(paste0(ref.values.data.path,"HOLPA data post-processing.xlsx"),sheet=paste0("ZWE","_inputs"))
    iso <- "ZWE"
  }
  assign("d",d,envir=.GlobalEnv)
  assign("ref_values_country",ref_values_country,envir=.GlobalEnv)
  assign("iso",iso,envir=.GlobalEnv)
}

set_d(country)

d <- d %>%
  mutate(module = ifelse(indicator %in% c("extra_economic_diversification/economic","extra_participation"), "performance", module)) %>%
  mutate(subindicator = ifelse(is.na(subindicator),indicator,subindicator)) %>%
  mutate(subindicator_label = "") %>%
  mutate(score = ifelse(score_agroecology_module=="no_answer",NA,score_agroecology_module)) %>%
  mutate(score = as.numeric(score)) %>% 
  mutate(score_label = label_score_agroecology_module) %>%
  mutate(indicator_order = ifelse(module=="agroecology",sub('_.*', "", indicator),NA)) %>%
  mutate(indicator_order = as.numeric(indicator_order)) %>%
  select(-c(label_score_agroecology_module, score_agroecology_module))

```

## Make functions to make plots for rapid viewing of data as code runs
```{r plot functions, include=FALSE, echo=FALSE}

col.theme <- c("agricultural"="#305127", "environmental"= "#699E5C", "social" = "#511F47" , "economic"= "#B36971")

#data <- d
#kpi <- "kpi1_crop_health"
kpi_histogram <- function(data, kpi){
  
  subindicator_label <- data %>% filter(indicator %in% c(kpi)) %>% select(subindicator_label) %>% unique()
  subindicator_label <- subindicator_label[1,1]
  
  g <- ggplot(data %>% filter(indicator %in% c(kpi) & !is.na(score)),aes(x=score))+
    geom_histogram()+ 
    coord_cartesian(expand=c(0))+
    ggtitle(paste0(subindicator_label, " in ",country))+ labs(x="")+
    theme_classic()+ theme(plot.title = element_text(hjust=0.5))
  print(g)
}

kpi_all_histogram <- function(data){
   data <- data %>%
    mutate(subindicator_label = factor(subindicator_label,levels=unique(subindicator_label[order(indicator_order)]))) %>%
     mutate(kpi_label= paste0(gsub("(.+?)(\\_.*)","\\1", indicator),": ",subindicator_label)) %>%
     mutate(kpi_label = factor(kpi_label, levels=unique(kpi_label[order(indicator_order)])))
     
  g <- ggplot(data %>% filter(module %in% c("performance kpi") & !is.na(score)), aes(x=score))+  
  ggtitle(paste0("KPIs for ",country," (n = ",length(unique(data$kobo_farmer_id)), ")"))+labs(x="")+
  geom_histogram()+ coord_cartesian(expand=c(0))+
      facet_wrap(~kpi_label, labeller=labeller(kpi_label = label_wrap_gen(40)), scale="free",strip.position=c("bottom"))+ 
    theme_classic()+ theme(plot.title = element_text(hjust=0.5),  strip.background = element_blank(),strip.placement = c("outside"))
  print(g)
}

kpi_all_boxplot <- function(data){
   data <- data %>%
    mutate(subindicator_label = factor(subindicator_label,levels=unique(subindicator_label[order(indicator_order)]))) %>%
     mutate(kpi_label= paste0(gsub("(.+?)(\\_.*)","\\1", indicator),": ",subindicator_label)) %>%
     mutate(kpi_label = factor(kpi_label, levels=unique(kpi_label[order(indicator_order)])))
     
  g <- ggplot(data %>% filter(module %in% c("performance kpi") & !is.na(score)), aes(y=score,x=factor(indicator,levels=unique(indicator[order(indicator_order)])), fill=theme))+ # geom_histogram()+  
  ggtitle(paste0("KPIs for ",country," (n = ",length(unique(ae_scores$kobo_farmer_id)), ")"))+labs(x="")+
  geom_boxplot()+  geom_count()+ scale_fill_manual(values=terrain.colors(5))+
  facet_wrap(~indicator, scale="free")+
  #facet_wrap(~kpi_label, labeller=labeller(kpi_label = label_wrap_gen(40)), scale="free",strip.position=c("bottom"))+
    theme_classic()+ theme(plot.title = element_text(hjust=0.5), axis.text.x = element_blank(), strip.background = element_blank(),strip.placement = c("outside"))
  print(g)
}

kpi_all_barchart <- function(data){
  
  data <- data %>%
     filter(!is.na(theme)) %>%
     group_by(theme,indicator,indicator_order) %>%
     summarise(score_scaled_mean = mean(score_scaled,na.rm=TRUE),
               score_scaled_sd = sd(score_scaled,na.rm=TRUE),
               score_scaled_med = median(score_scaled,na.rm=TRUE)) %>%
     mutate(score_scaled_mean_unattained = ifelse(between(score_scaled_mean,0,100), 100-score_scaled_mean,NA)) %>% 
     arrange(indicator_order) %>%
     mutate(indicator = factor(indicator, levels = unique(indicator[order(as.numeric(indicator_order))])))
  
    g <- ggplot(data %>% filter(!is.na(score_scaled_mean)), aes(x=score_scaled_mean,y=reorder(indicator,score_scaled_mean),fill=theme))+
    geom_col(width=0.5,show.legend=TRUE) + 
    geom_errorbar(aes(x=score_scaled_mean, 
                      xmin=ifelse(score_scaled_mean - score_scaled_sd >=0, score_scaled_mean - score_scaled_sd , 0), 
                      xmax=ifelse(score_scaled_mean + score_scaled_sd<=100, score_scaled_mean + score_scaled_sd, 100)),linewidth=0.5,colour="grey50", width=0.2)+
    geom_text(aes(label=round(score_scaled_mean,0),colour=theme), hjust=0,size=5,fontface="bold",show.legend=FALSE)+
    ggtitle(paste0("KPIs for ",country))+labs(x="KPI score (scaled from 0-100)")+
    coord_cartesian(expand=c(0),clip="off")+
    scale_x_continuous(breaks=seq(0,100,20),limits=c(0,110))+
    scale_fill_manual(values=col.theme)+
    scale_colour_manual(values=col.theme)+
    theme_classic()+ 
    theme(plot.title = element_text(hjust=0.5),
          axis.title.y=element_blank(), 
          legend.position="bottom")
  print(g)  
}

kpi_all_gauge <- function(data){
   data <- data %>%
     filter(!is.na(theme)) %>%
    mutate(subindicator_label = factor(subindicator_label,levels=unique(subindicator_label[order(indicator_order)]))) %>%
     mutate(score_scaled = ifelse(between(score_scaled,0,100), score_scaled,NA)) %>%
     group_by(theme,indicator,indicator_order,kpi_order, kpi_label, kpi_label_short) %>%
     summarise(score_scaled_mean = mean(score_scaled,na.rm=TRUE),
               score_scaled_sd = sd(score_scaled,na.rm=TRUE),
               score_scaled_med = median(score_scaled,na.rm=TRUE)) %>%
     mutate(score_scaled_mean_unattained = ifelse(between(score_scaled_mean,0,100), 100-score_scaled_mean,NA)) %>% 
     #arrange(kpi_order) %>%
     mutate(indicator = factor(indicator, levels = unique(indicator[order(indicator_order)]))) %>%
     mutate(kpi_order = factor(kpi_order,levels=unique(kpi_order[order(indicator_order)]))) %>%
     mutate(kpi_label_short = factor(str_wrap(kpi_label_short,20), levels=unique(str_wrap(kpi_label_short,20)[order(indicator_order)])))
     
  g <- ggplot(data %>% filter(!is.na(score_scaled_mean)))+
    # part showing score scaled from 0 to 100%
    geom_arc_bar(aes(x0=1,y0=1, 
                   start= (score_scaled_mean/100)*(2*pi),
                   end=((score_scaled_mean/100)*(2*pi))+((score_scaled_mean_unattained/100)*(2*pi)),
                   r0=0.75,r=1),
                 fill="grey80",colour="white",show.legend=FALSE)+
    # colour in the gap between score and 100%
    geom_arc_bar(aes(x0=1,y0=1, 
                   start=0,
                   end = (score_scaled_mean/100)*2*pi,
                   r0=0.75,r=1, fill=theme), colour="white", show.legend=FALSE) + 
        
    geom_text(aes(x=1,y=1,label=round(score_scaled_mean,0),colour=theme),
             size=5,fontface="bold",vjust=0.5,show.legend=FALSE)+
    coord_fixed()+
    ggtitle(paste0("KPIs for ",country," scaled from 0 (undesirable) to 100 (desirable)"))+labs(x="")+
    scale_fill_manual(values=col.theme)+
    scale_colour_manual(values=col.theme)+
    # add labels in centre
    facet_wrap(~factor(kpi_order,levels=unique(kpi_order[order(indicator_order)])), strip.position=c("bottom"))+
    #facet_wrap(~factor(kpi_label_short, levels=unique(kpi_label_short[order(indicator_order)])), strip.position=c("bottom"))+
    theme_void()+ 
      theme(plot.title = element_text(hjust=0.5), strip.background = element_blank())
  print(g)
  
}

```


## Calculate agroecology indicator scores
Agroecology adherence indicator scores are pre-calculated in another code.

```{r agroecology indicator calcs, include=TRUE, echo=FALSE}
#### Overall agroecology score ####

ae_scores <- d %>%
  filter(module == "agroecology" & !is.na(score)) %>%
  group_by(kobo_farmer_id,module, indicator, indicator_order) %>%
  summarise(score = median(score,na.rm=TRUE),
            score_mean = mean(score,na.rm=TRUE),
            score_sum = sum(score,na.rm=TRUE),
            score_count = n(),.groups="keep") 

ae_calc_temp <- ae_scores %>%
  group_by(kobo_farmer_id,module) %>%
  summarise(score = median(score,na.rm=TRUE)) %>%
  mutate(indicator = "score_ae_overall",
         indicator_order=14)

ae_scores<- ae_scores %>% full_join(ae_calc_temp)

d <- d %>% full_join(ae_calc_temp)

ggplot(ae_scores, aes(y=score, x=factor(indicator,levels=unique(indicator[order(indicator_order)])), fill=factor(indicator,levels=unique(indicator[order(indicator_order)]))))+ 
  geom_boxplot()+ geom_count()+ 
  ggtitle(paste0("Agroecology scores for ",country," (n = ",length(unique(ae_scores$kobo_farmer_id)), ")")) + 
  labs(x="")+ 
  scale_fill_manual(values=c(terrain.colors(14)[1:13],"purple3"),name="Indicators")+
  theme_bw()+ theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5),plot.title=element_text(hjust=0.5))

ggsave(paste0(global.data.path,"figures/1_agroecology_scores_",country,".tif"),width=7,height=6,units="in")

```
## Calculate Key Performance Indicator scores
Key performance indicator scores are calculated here from survey responses.

```{r KPI calcs, include=TRUE, echo=FALSE}

#### Performance KPI1 crop health ###

#sort(unique(d$indicator))
#temp <- d %>% filter(indicator =="crop_health")
#temp <- d %>% filter(indicator =="crop_health_fw")
#temp <- d %>% filter(grepl("What percentage of the total crop production",label_question))

#table(temp$label_question)
#table(temp$name_question)
#table(temp$label_question,temp$name_question)

d <- d %>% 
  mutate(subindicator = ifelse(grepl("What percentage of the total crop production was lost or damaged",label_question), "crop_loss",subindicator)) %>%
  mutate(subindicator = ifelse(grepl("What was the main cause of crop loss or damage?",label_question), "crop_loss_cause", subindicator)) %>%
  
  #mutate(subindicator = ifelse(name_question =="_3_4_2_1_8_2","crop_loss",
  #                             ifelse(name_question == "_3_4_2_1_8_3","crop_loss_cause",subindicator))) %>%
  
  mutate(subindicator_label = ifelse(subindicator=="crop_loss", "Avoided crop production lost or damaged in last 12 months (%)", subindicator_label)) %>% 
  mutate(indicator = ifelse(subindicator %in% c("crop_loss"), "kpi1_crop_health", indicator)) %>%
    mutate(indicator_order = ifelse(indicator %in% c("kpi1_crop_health"), 1, indicator_order))

# Remove out of bounds responses
temp_kpi_calc <- d %>%
  filter(subindicator %in% c("crop_loss")) %>%
  mutate(score = ifelse(indicator %in% c("kpi1_crop_health"), name_choice, score)) %>%
  mutate(score = as.numeric(score)) %>%
  # Compute 100 - % loss, so that higher values are better ('Avoided crop loss')
  mutate(score = ifelse(indicator %in%  c("kpi1_crop_health") & score>100,0,100-score)) %>%
  mutate(module = ifelse(indicator %in%  c("kpi1_crop_health"),"performance kpi",module)) 

kpi_scores <- temp_kpi_calc %>% 
  select(kobo_farmer_id,country, module, theme, indicator, indicator_order, subindicator, subindicator_label, name_question,label_question, name_choice,label_choice,score,score_label)

kpi_histogram(kpi_scores,"kpi1_crop_health")
#kpi_all_boxplot(kpi_scores)

### Performance KPI1b Crop health from fieldwork ####
#sort(unique(d$indicator))
#temp <- d %>% filter(indicator =="crop_health_fw") %>% filter(!is.na(name_choice))
#table(temp$label_question)
#table(temp$name_question)
#table(temp$label_question,temp$name_question)

temp_kpi_calc <- d %>% filter(indicator =="crop_health_fw") %>% filter(!is.na(name_choice)) %>%
  mutate(subindicator = gsub("\\_.*", "\\1", name_choice),
         score = as.numeric(gsub(".*_(*)", "\\1", name_choice)),
         label_question = gsub("^([^_]*_[^_]*_[^_]*)_.*$","\\1",name_question)) %>%
         #label_question = gsub(".*_.*_(.*)$","\\1",name_question)) %>%
  mutate(subindicator = ifelse(subindicator == "apperance","appearance",subindicator )) %>% unique() %>%
  dcast(kobo_farmer_id+country+label_question~subindicator,value.var="score",fun=median) %>%
  
  # assign scores from 1 to 5 noting response 0 means "I am not sure, or the question is not applicable" 
  mutate_at(c("appearance" ,    "appearance", "disease"  ,      "enemy"  ,        "growth" ,        "management"  ,   "natural", "pest"  , "weed"  ),~na_if(.,0))  %>%
  rowwise() %>%
  mutate(score = median(c(appearance , disease ,      enemy  ,   growth ,        management ,   natural, pest  , weed ),na.rm=T)) %>%
  group_by(kobo_farmer_id,country) %>%
  summarise(score = median(score,na.rm=T)) %>%
  
  # add indicator name
  mutate(indicator = "kpi1b_crop_health_fieldwork",
         subindicator = "crop_health_fw",
         subindicator_label = "Crop health assessed in-field on a scale of 1 (unhealthy) to 5 (healthy)",
         indicator_order = 1.2) 

kpi_scores <- kpi_scores %>% full_join(temp_kpi_calc) %>%
  mutate(module = ifelse(indicator %in% c("kpi1b_crop_health_fieldwork"),"performance kpi",module)) %>% mutate(theme = ifelse(indicator %in% c("kpi1b_crop_health_fieldwork"),"agricultural",theme))

kpi_histogram(kpi_scores,"kpi1b_crop_health_fieldwork")
#kpi_all_boxplot(kpi_scores)

### Performance KPI2 animal health ####
#sort(unique(d$indicator))
#temp <- d %>% filter(indicator =="animal_health")
#table(temp$label_question)
#table(temp$name_choice)
#table(temp$label_choice)
#table(temp$name_question,temp$label_question)

d <- d %>% 
  mutate(subindicator = ifelse(label_question == "What was the extent of injury, illness or death of livestock due to diseases in the last 12 months","livestock_loss",
                               ifelse(label_question=="Over the past 12 months [add country meaning], how did you manage livestock diseases","livestock_disease_management",subindicator))) %>%
  #mutate(subindicator = ifelse(name_question %in% c( "_1_4_3_8/1","_1_4_3_8/2","_1_4_3_8/3","_1_4_3_8/4","_1_4_3_8/5","_1_4_3_8/6","_1_4_3_8/7","_1_4_3_8/8"),"livestock_loss", ifelse(name_question %in% c("_1_4_3_8/1","_1_4_3_8/2","_1_4_3_8/3","_1_4_3_8/4","_1_4_3_8/5","_1_4_3_8/6","_1_4_3_8/7","_1_4_3_8/8"),"livestock_disease_management",subindicator))) %>%
    mutate(subindicator_label = ifelse(subindicator=="livestock_loss","Extent of livestock injury, illness or death due to diseases in last 12 months (score 1-5)",subindicator_label)) 

temp_kpi_calc <- d %>%
  mutate(score = ifelse(subindicator =="livestock_loss" & label_choice=="None",5,
                        ifelse(subindicator =="livestock_loss" & label_choice=="Low",3.66,
                               ifelse(subindicator =="livestock_loss" & label_choice=="Medium",2.33,
                                      ifelse(subindicator =="livestock_loss" & label_choice=="High",1, as.numeric(score)))))) %>%
  
  mutate(score_label = ifelse(subindicator =="livestock_loss" & label_choice=="None","No livestock injury, illness or death",
                        ifelse(subindicator =="livestock_loss" & label_choice=="Low","Low level of livestock injury, illness or death",
                               ifelse(subindicator =="livestock_loss" & label_choice=="Medium","Medium level of livestock injury, illness or death",
                                      ifelse(subindicator =="livestock_loss" & label_choice=="High","High level of livestock injury, illness or death",score_label))))) %>%
  
  mutate(indicator = ifelse(subindicator=="livestock_loss" & module=="performance","kpi2_animal_health",indicator)) %>%
  mutate(indicator_order = ifelse(indicator =="kpi2_animal_health", 2, indicator_order))  %>%
  mutate(module = ifelse(indicator == "kpi2_animal_health","performance kpi",module)) %>% mutate(theme = ifelse(indicator %in% c("kpi2_animal_health"),"agricultural",theme)) %>%
  filter(indicator=="kpi2_animal_health")

#kpi_scores <-  temp_kpi_calc # For Senegal - temporary fix
kpi_scores <-  kpi_scores %>% full_join(temp_kpi_calc)

kpi_histogram(kpi_scores,"kpi2_animal_health")
#kpi_all_boxplot(kpi_scores)

### Performance KPI3 soil health ####
#temp <- d %>% filter(indicator =="soil_health")
#table(temp$label_question)
#table(temp$subindicator)
#table(temp$name_choice,temp$label_question)
#table(temp$label_choice,temp$name_choice)
#table(temp$label_choice_short,temp$name_choice)
#table(temp$label_choice_short,temp$score)

d <- d %>% 
  mutate(subindicator = ifelse(label_question == "How would you describe the fertility of your soil on your farmland?","soil_fertility",
                               ifelse(label_question=="How would you describe the level of soil erosion problem on your farmland?","soil_erosion",subindicator))) %>%
  
  # NOTE that soil erosion label_choice is the 'wrong' way around, i.e. lower scores are better         
  mutate(score = ifelse(subindicator=="soil_erosion" & name_choice=="0",5,
                        ifelse(subindicator=="soil_erosion" & name_choice=="1",3,
                               ifelse(subindicator=="soil_erosion" & name_choice=="2",1,score)))) %>%
  
  # soil fertility
  mutate(score = ifelse(subindicator=="soil_fertility" & name_choice=="0",1,
                        ifelse(subindicator=="soil_fertility" & name_choice=="1",2.33,
                               ifelse(subindicator=="soil_fertility" & name_choice=="2",3.66,
                                      ifelse(subindicator=="soil_fertility" & name_choice=="3",5,score)))))

# combine soil erosion and fertility scores
temp_kpi_calc <- d %>% filter(subindicator %in% c("soil_erosion","soil_fertility")) %>%
  mutate(score = as.numeric(score)) %>%
  group_by(kobo_farmer_id,country) %>%
  summarise(score = median(score,na.rm=TRUE)) %>%
  mutate(indicator = "kpi3_soil_health",
         subindicator = "soil_health_overall")

kpi_scores <- kpi_scores %>% full_join(temp_kpi_calc, by = c("kobo_farmer_id", "country", "indicator", "subindicator", "score")) %>%
  mutate(subindicator_label = ifelse(subindicator=="soil_health_overall","Perceived soil erosion and fertility from 1 (infertile and major soil erosion) to 3 (highly fertile with no soil erosion)",subindicator_label)) %>%
  mutate(indicator_order = ifelse(indicator =="kpi3_soil_health",3,indicator_order)) %>%
  mutate(module = ifelse(indicator == "kpi3_soil_health","performance kpi",module)) %>% mutate(theme = ifelse(indicator == "kpi3_soil_health","agricultural",theme))
  
kpi_histogram(kpi_scores,"kpi3_soil_health")
#kpi_all_boxplot(kpi_scores)

### Performance KPI3b soil carbon from fieldwork - NEEDS COMPLETING ####

### Performance KPI4 nutrient use ratio ####
#sort(unique(d$indicator))
#temp <- d %>% filter(indicator =="nutrient_use") # or inputs
#sort(unique(temp$subindicator))
#sort(unique(temp$label_question))

# set reference fertiliser use (kg/ha) used as the benchmark to determine the under or over use of fertilizer
# default is -9999 meaning NO DATA, and in this case the MEDIAN fertilizer use in the country-specific HOLPA survey data is used

# activate this only if information in ref_values_country on fertilizer recommendations covers enough crops to justify using an average across all crops
if(iso %in% c("ZWE")){
ref_nut_quantity_kg_ha <- ref_values_country %>%
  select(nut_ref_rainfed_clean,nut_ref_irr_clean) %>%
  summarise(nut_ref_med = median(nut_ref_rainfed_clean,na.rm=TRUE),
            nut_ref_mean = mean(nut_ref_rainfed_clean,na.rm=TRUE)) %>%
  mutate(nut_ref_med = ifelse(is.na(nut_ref_med),-9999,nut_ref_med))
ref_nut_quantity_kg_ha <- ref_nut_quantity_kg_ha$nut_ref_med
} else{
  ref_nut_quantity_kg_ha <- -9999 
}

nut_conversion_factors <- ref_values_nut %>%
  filter(Region == iso) %>%
  rename("fertilizer_unit" = `fertilizer unit`,
    "conversion_factor" = `conversion factor (to convert to kilograms)`) %>%
  select(fertilizer_unit,conversion_type_clean,conversion_factor) %>%
  mutate(conversion_factor = ifelse(is.na(conversion_factor),-9999,conversion_factor))

temp_kpi_calc1 <- d %>% filter(indicator =="nutrient_use") %>% filter(label_question =="Over the past 12 months [add country meaning], how much CHEMICAL FERTILIZER was applied to cropland: Specify the surface area affected in ${_1_4_1_1_calculate}") %>% select(kobo_farmer_id, label_choice) %>% unique() %>% rename("nut_chem_area_unit"=label_choice) 

temp_kpi_calc2 <- d %>% filter(indicator =="nutrient_use") %>% filter(label_question =="Over the past 12 months [add country meaning], how much ORGANIC FERTILIZER OR MANURE GENERATED ON-FARM was applied to cropland: Specify the surface area affected in ${_1_4_1_1_calculate}") %>% select(kobo_farmer_id, label_choice) %>% unique() %>% rename("nut_orgF_area_unit"=label_choice)  

temp_kpi_calc3 <- d %>% filter(indicator =="nutrient_use") %>% filter(label_question =="Over the past 12 months [add country meaning], how much ORGANIC FERTILIZER OR MANURE FROM OTHER SOURCES (e.g. puchased) was applied to cropland: Specify the surface area affected in ${_1_4_1_1_calculate}") %>% select(kobo_farmer_id, label_choice) %>% unique() %>% rename("nut_org_area_unit"=label_choice)  

area_unit <- temp_kpi_calc1 %>% left_join(temp_kpi_calc2) %>% left_join(temp_kpi_calc3)

if(iso %in% c("SEN")){
  area_unit <- area_unit %>%
    mutate_at(c("nut_chem_area_unit","nut_org_area_unit","nut_orgF_area_unit"),
               ~ifelse(is.na(.),"hectares",as.character(.)))
}

if(iso %in% c("ZWE")){
  area_unit <- area_unit %>%
    mutate_at(c("nut_chem_area_unit","nut_org_area_unit","nut_orgF_area_unit"),
               ~ifelse(is.na(.),"acres",as.character(.)))
}

d <- d %>% 
  # chemical fertilizers
  mutate(subindicator = ifelse(label_question == "Over the past 12 months [add country meaning], how much CHEMICAL FERTILIZER was applied to cropland: Specify applied unit:","nut_chem_unit",subindicator)) %>%
  mutate(subindicator = ifelse(label_question=="Over the past 12 months [add country meaning], how much CHEMICAL FERTILIZER was applied to cropland: Specify the amount applied","nut_chem_quantity",subindicator)) %>%
  mutate(subindicator = ifelse(label_question=="Over the past 12 months [add country meaning], how much CHEMICAL FERTILIZER was applied to cropland: Specify the surface area affected in ${_1_4_1_1_calculate}","nut_chem_area",subindicator)) %>%
  
  # organic fertilisers generated on-farm
  mutate(subindicator = ifelse(label_question == "Over the past 12 months [add country meaning], how much ORGANIC FERTILIZER OR MANURE GENERATED ON-FARM was applied to cropland: Specify applied unit:" ,"nut_orgF_unit",subindicator))  %>%
  mutate(subindicator = ifelse(label_question == "Over the past 12 months [add country meaning], how much ORGANIC FERTILIZER OR MANURE GENERATED ON-FARM was applied to cropland: Specify the amount applied:","nut_orgF_quantity",subindicator)) %>%
  mutate(subindicator = ifelse(label_question == "Over the past 12 months [add country meaning], how much ORGANIC FERTILIZER OR MANURE GENERATED ON-FARM was applied to cropland: Specify the surface area affected in ${_1_4_1_1_calculate}" , "nut_orgF_area",subindicator)) %>%
  
  # organic fertilizers from other sources
    mutate(subindicator = ifelse(label_question == "Over the past 12 months [add country meaning], how much ORGANIC FERTILIZER OR MANURE FROM OTHER SOURCES (e.g. puchased) was applied to cropland: Specify applied unit:","nut_org_unit",subindicator))  %>%
  mutate(subindicator = ifelse(label_question == "Over the past 12 months [add country meaning], how much ORGANIC FERTILIZER OR MANURE FROM OTHER SOURCES (e.g. puchased) was applied to cropland: Specify the amount applied" ,"nut_org_quantity",subindicator)) %>%
  mutate(subindicator = ifelse(label_question == "Over the past 12 months [add country meaning], how much ORGANIC FERTILIZER OR MANURE FROM OTHER SOURCES (e.g. puchased) was applied to cropland: Specify the surface area affected in ${_1_4_1_1_calculate}","nut_org_area",subindicator)) 

# Put into wide format to align associated data
temp_kpi_calc <- d %>% filter(indicator =="nutrient_use") %>%
  filter(subindicator %in% c("nut_chem_unit","nut_chem_quantity","nut_chem_area",
                             "nut_orgF_unit","nut_orgF_quantity","nut_orgF_area",
                             "nut_org_unit","nut_org_quantity","nut_org_area")) %>%
  dcast(kobo_farmer_id+country+indicator ~subindicator,value.var="name_choice") 

# Check which fertilizer units are used
sort(unique(temp_kpi_calc$nut_chem_unit))
sort(unique(temp_kpi_calc$nut_org_unit))
sort(unique(temp_kpi_calc$nut_orgF_unit))

temp_kpi_calc <- temp_kpi_calc %>%
    left_join(nut_conversion_factors[,c("fertilizer_unit","conversion_factor")],by=c("nut_chem_unit"="fertilizer_unit")) %>%
  rename("nut_chem_unit_conversion" = conversion_factor) %>%
  left_join(nut_conversion_factors[,c("fertilizer_unit","conversion_factor")],by=c("nut_orgF_unit"="fertilizer_unit")) %>%
  rename("nut_orgF_unit_conversion" = conversion_factor) %>%
  left_join(nut_conversion_factors[,c("fertilizer_unit","conversion_factor")],by=c("nut_org_unit"="fertilizer_unit")) %>%
  rename("nut_org_unit_conversion" = conversion_factor) %>%
  left_join(area_unit) %>%
  
  # set conversion factor to 1 if unit is kilograms
  mutate(nut_chem_unit_conversion = ifelse(nut_chem_unit %in% c("kilograms","kg","Kilograms","Kilogram","kilogram","Kilogrammes","kilogramme"),1,nut_chem_unit_conversion),
         nut_org_unit_conversion = ifelse(nut_org_unit %in% c("kilograms","kg","Kilograms","Kilogram","kilogram","Kilogrammes","kilogramme"),1,nut_org_unit_conversion),
nut_orgF_unit_conversion = ifelse(nut_orgF_unit %in% c("kilograms","kg","Kilograms","Kilogram","kilogram","Kilogrammes","kilogramme"),1,nut_orgF_unit_conversion)) %>%
  
   # set quantities to 0 if there is no information on area unit, or no conversion factor provided
  mutate(nut_chem_quantity = ifelse(nut_chem_quantity>0 & (is.na(nut_chem_area) | nut_chem_area ==0 | is.na(nut_chem_unit_conversion) | nut_chem_unit_conversion<0),0,nut_chem_quantity),
         nut_org_quantity = ifelse(nut_org_quantity>0 & (is.na(nut_org_area) | nut_org_area ==0 | is.na(nut_org_unit_conversion) | nut_org_unit_conversion<0),0,nut_org_quantity),
         nut_orgF_quantity = ifelse(nut_orgF_quantity>0 & (is.na(nut_orgF_area)| nut_orgF_area ==0 | is.na(nut_orgF_unit_conversion) | nut_orgF_unit_conversion<0),0,nut_orgF_quantity)) %>%
  
  # fix missing area unit in Kenya data
  mutate(nut_orgF_area_unit = ifelse(kobo_farmer_id== 286788734,"acre",nut_orgF_area_unit)) 

# Calculate nutrient use per unit area
temp_kpi_calc <- temp_kpi_calc %>%
    mutate_at(c("nut_chem_quantity","nut_chem_area",
              "nut_org_quantity","nut_org_area",
              "nut_orgF_quantity","nut_orgF_area"), 
              ~ifelse(is.na(.),0,as.numeric(.))) %>%
  ungroup() %>%
    mutate_at(c("nut_chem_unit_conversion","nut_org_unit_conversion","nut_orgF_unit_conversion"), ~ifelse(is.na(.),NA,as.numeric(.))) %>%
  mutate_at(c("nut_chem_unit_conversion","nut_org_unit_conversion","nut_orgF_unit_conversion"), ~ifelse((.)==-9999,NA,(.))) 

temp_kpi_calc <- temp_kpi_calc %>%
  # convert areas into hectares
  mutate(nut_chem_area_ha = ifelse(nut_chem_area_unit %in% c("acre", "acres","in acres","Acres"), nut_chem_area * acre_to_hectare, nut_chem_area),
         nut_orgF_area_ha = ifelse(nut_orgF_area_unit %in% c("acre","acres","in acres","Acres"), nut_orgF_area * acre_to_hectare, nut_orgF_area),
         nut_org_area_ha = ifelse(nut_org_area_unit %in% c("acre","acres","in acres","Acres"), nut_org_area * acre_to_hectare, nut_org_area)) %>%
  
  # convert quantities applied into kg
  mutate(nut_chem_kg_ha = ifelse(nut_chem_quantity>0, (nut_chem_quantity*nut_chem_unit_conversion) /nut_chem_area_ha, 0),
         nut_org_kg_ha = ifelse(nut_org_quantity>0, (nut_org_quantity*nut_org_unit_conversion)/nut_org_area_ha, 0),
         nut_orgF_kg_ha = ifelse(nut_orgF_quantity>0, (nut_orgF_quantity*nut_orgF_unit_conversion)/nut_orgF_area_ha, 0)) %>%
  
  # Combine and convert from kg/area to kg/hectare
  mutate(nut_quantity_kg_ha = nut_chem_kg_ha + nut_org_kg_ha + nut_orgF_kg_ha) 

# Calculate ratio of nutrient use to recommended (or median) nutrient use levels
temp_kpi_calc <- temp_kpi_calc %>%
  group_by(country) %>% mutate(med_nut_quantity_kg_ha = median(nut_quantity_kg_ha, na.rm=T), mean_nut_quantity_kg_ha = mean(nut_quantity_kg_ha, na.rm=T)) %>% ungroup()  %>%
  mutate(ref_nut_quantity_kg_ha = ref_nut_quantity_kg_ha) %>%
  mutate(score =  ifelse(ref_nut_quantity_kg_ha > 0 , nut_quantity_kg_ha/ref_nut_quantity_kg_ha, nut_quantity_kg_ha/med_nut_quantity_kg_ha)) 

# NOTE, over use of fertilizers receives the highest score, and under use the lowest. 
# this is an agricultural KPI, so we are interested in having both adequate nutrient applications and no over-use (less efficiency)
# so need to be careful with scaling this indicator

# Add this back into the main dataset
temp_kpi_calc <- temp_kpi_calc %>% mutate(indicator = "kpi4_nutrient_use",
                                          subindicator = "nutrient_use", 
                                          score = as.numeric(score)) %>%
    select(kobo_farmer_id,country,indicator,subindicator,score)

kpi_scores <- kpi_scores %>% full_join(temp_kpi_calc, by = c("kobo_farmer_id", "country", "indicator", "subindicator", "score"), keep=NULL) %>%
  mutate(subindicator_label = ifelse(indicator %in% c("kpi4_nutrient_use"),"Ratio between recorded and reference fertilizer use (kg/ha)",subindicator_label),
         indicator_order = ifelse(indicator %in% c("kpi4_nutrient_use"),4,indicator_order)) %>%
    mutate(module = ifelse(indicator %in% c("kpi4_nutrient_use"),"performance kpi",module)) %>%
  mutate(theme = ifelse(indicator %in% c("kpi4_nutrient_use"),"agricultural",theme))

kpi_histogram(kpi_scores,"kpi4_nutrient_use")
#kpi_all_boxplot(kpi_scores)

### Performance KPI5a biodiversity - animals ####
#table(d$indicator,d$module)
#temp <- d %>% filter(indicator %in% c("biodiversity_diversity","biodiversity_abundance"))
#sort(unique(temp$label_question))

d <- d %>% 
  # insect pollinators
  mutate(subindicator = ifelse(label_question == "How would you describe the diversity of insect pollinators on your farm?","bio_pollinators",subindicator)) %>%
  # pests
  mutate(subindicator = ifelse(label_question=="How would you describe the diversity of crop and livestock pests on your farm?","bio_pests",subindicator)) %>%
  # pest enemies
  mutate(subindicator = ifelse(label_question=="How would you describe the diversity of natural crop and livestock pest enemies on your farm?","bio_enemies",subindicator)) %>%
  # mammals
    mutate(subindicator = ifelse(label_question=="How would you describe the diversity of mammals on your farm?"  ,"bio_mammals",subindicator)) 
  
  # assign scores
temp_kpi_calc <- d %>%
  mutate(score = case_when(
      subindicator %in% c("bio_pollinators","bio_pests","bio_enemies","bio_mammals") & name_choice %in% ("none") ~ 1,
      subindicator %in% c("bio_pollinators","bio_pests","bio_enemies","bio_mammals") & name_choice %in% ("low") ~ 2.33, 
      subindicator %in% c("bio_pollinators","bio_pests","bio_enemies","bio_mammals") & name_choice %in% ("medium") ~ 3.66, 
      subindicator %in% c("bio_pollinators","bio_pests","bio_enemies","bio_mammals") & name_choice %in% ("high") ~ 5,   .default = score)) %>% 
  
  # assign score labels
  mutate(score_label = case_when(
      subindicator %in% c("bio_pollinators","bio_pests","bio_enemies","bio_mammals") & name_choice %in% ("none") ~ "None: no animals observed",
      subindicator %in% c("bio_pollinators","bio_pests","bio_enemies","bio_mammals") & name_choice %in% ("low") ~ "Low: animals rarely seen or limited to a few species", 
      subindicator %in% c("bio_pollinators","bio_pests","bio_enemies","bio_mammals") & name_choice %in% ("medium") ~ "Medium: animals regularly seen with several species", 
      subindicator %in% c("bio_pollinators","bio_pests","bio_enemies","bio_mammals") & name_choice %in% ("high") ~ "High: abundant with a wide varity of species",   .default = score_label))
      
temp_kpi_calc <- temp_kpi_calc %>% filter(subindicator %in% c("bio_pollinators","bio_pests","bio_enemies","bio_mammals")) %>%
#dcast(kobo_farmer_id+country+indicator ~subindicator,value.var="score") %>%
  group_by(kobo_farmer_id,country) %>%
  summarise(score = median(score,na.rm=TRUE)) %>%
  mutate(indicator = "kpi5a_animal_diversity",
         subindicator = "animal_diversity") %>% 
    mutate(subindicator_label = "Animal diversity from 1 (no animals observed) to 5 (animals abundant with a wide varity of species)")

kpi_scores <- kpi_scores %>% full_join(temp_kpi_calc, by = c("kobo_farmer_id", "country", "indicator", "subindicator","subindicator_label","score"), keep=NULL) %>%
  mutate(indicator_order = ifelse(indicator =="kpi5a_animal_diversity",5.1,indicator_order)) %>%
    mutate(module = ifelse(indicator == "kpi5a_animal_diversity","performance kpi",module)) %>%
    mutate(theme = ifelse(indicator == "kpi5a_animal_diversity","environmental",theme))

kpi_histogram(kpi_scores,"kpi5a_animal_diversity")
#kpi_all_boxplot(kpi_scores)

### Performance KPI5b biodiversity - trees ####

d <- d %>% 
  # tree abundance
  mutate(subindicator = ifelse(label_question == "How would you describe the amount of trees (or perennial woody plants) on your farm?","bio_tree_abun",subindicator)) %>%
  # tree diversity
    mutate(subindicator = ifelse(label_question== "How would you describe the diversity of trees (or perennial woody plants) on your farm?" , "bio_tree_diversity",subindicator))
  
#temp_kpi_calc <- d %>% filter(subindicator %in% c("bio_tree_abun","bio_tree_diversity"))
#unique(temp_kpi_calc$name_choice)

# assign scores
temp_kpi_calc <- d %>%
  mutate(score = case_when(
      subindicator %in% c("bio_tree_abun","bio_tree_diversity") & name_choice %in% ("none") ~ 1,
      subindicator %in% c("bio_tree_abun","bio_tree_diversity") & name_choice %in% ("low") ~ 2.33, 
      subindicator %in% c("bio_tree_abun","bio_tree_diversity") & name_choice %in% ("medium") ~ 3.66, 
      subindicator %in% c("bio_tree_abun","bio_tree_diversity") & name_choice %in% ("high") ~ 5,   .default = score)) 
      
temp_kpi_calc <- temp_kpi_calc %>% filter(subindicator %in% c("bio_tree_abun","bio_tree_diversity")) %>%
#dcast(kobo_farmer_id+country+indicator ~subindicator,value.var="score") %>%
  group_by(kobo_farmer_id,country) %>%
  summarise(score = median(score,na.rm=TRUE)) %>%
  mutate(indicator = "kpi5b_tree_diversity",
         subindicator = "tree_diversity") %>% 
    mutate(subindicator_label = "Tree diversity from 1 (no trees) to 5 (high tree diversity)")

kpi_scores <- kpi_scores %>% full_join(temp_kpi_calc, by = c("kobo_farmer_id", "country", "indicator", "subindicator","subindicator_label","score"), keep=NULL) %>%
  mutate(indicator_order = ifelse(indicator =="kpi5b_tree_diversity",5.2,indicator_order)) %>%
    mutate(module = ifelse(indicator == "kpi5b_tree_diversity","performance kpi",module)) %>%
    mutate(theme = ifelse(indicator == "kpi5b_tree_diversity","environmental",theme))

kpi_histogram(kpi_scores,"kpi5b_tree_diversity")
#kpi_all_boxplot(kpi_scores)

### Performance KPI6a biodiversity - abd crop species concentration ####
#table(d$indicator,d$module)
#temp <- d %>% filter(indicator %in% c("biodiversity_agrobiodiversity"))
#temp <- d %>% filter(indicator %in% c("6_synergy"))
#temp <- d %>% filter(indicator %in% c("productivity_crops"))
#temp <- d %>% filter(indicator %in% c("biodiversity_climate_mitigation"))
#unique(temp$label_question)
#unique(temp$name_choice)

# Extract unit used to measure production area
area_unit_crops <- d  %>% filter(label_question =="Area of land under ${_3_4_3_1_3_calculate} production in ${_1_4_1_1_calculate}:") %>% select(kobo_farmer_id, index, label_choice) %>% unique() %>% rename(area_unit = label_choice)
#area_unit_crops <- area_unit_crops$label_choice

# Extract species richness and production area for three main crops
d <- d %>% 
  # crop species richness
  mutate(subindicator = ifelse(label_question == "In the last 12 months [add country meaning], how many different crops species (including perennial crops) were produced on your farm","abd_crop_richness",subindicator)) %>%
  
  # total cropland area
  mutate(subindicator = ifelse(label_question == "What is the total area of land used for growing crops in ${_1_4_1_1_calculate}?", "abd_crop_area",subindicator))  %>%
  
  # area per crop
  mutate(subindicator = ifelse(label_question == "Name of main crop species","abd_crop_name",subindicator)) %>%
  mutate(subindicator = ifelse(label_question == "Area of land under ${_3_4_3_1_3_calculate} production in ${_1_4_1_1_calculate}:","abd_area_per_crop",subindicator)) %>%
  
  # crop variety - local/exotic 
  mutate(subindicator = ifelse(label_question == "Do the crops you grow come from certified quality seeds or locally adapted varieties (e.g. traditional cultivars, landraces)?"   ,"abd_crop_local",subindicator)) %>%
  
  # extract area of cropland under diversified practices
  mutate(subindicator = ifelse(label_question == "On the grazing land (owned, leased or shared), did you apply in the last 12 months any of the following practices?","abd_practices_pasture",subindicator)) %>%
  mutate(subindicator = ifelse(label_question == "Practices used on your cropland in the past [localised description of 12 months]","abd_practices_cropland", subindicator )) %>%
  mutate(subindicator = ifelse(label_question =="Provide the approximate area of land under this practice in hectares or acres:","abd_practices_area",subindicator )) %>%
  
  # correct indicator names
  mutate(indicator = ifelse(subindicator %in% c("abd_crop_name", "abd_area_per_crop","abd_crop_area","abd_crop_richness", "abd_practices_pasture", "abd_practices_cropland",  "abd_practices_area"), "biodiversity_agrobiodiversity",indicator)) 

# Extract total crop production area 
temp_kpi_calc1 <- d %>%
  filter(subindicator %in% c("abd_crop_name", "abd_area_per_crop")) %>%
  dcast(kobo_farmer_id+country+indicator+index~subindicator,value.var="name_choice") %>% 
  left_join(area_unit_crops)

temp_kpi_calc2 <- d %>%
  filter(subindicator %in% c("abd_crop_area","abd_crop_richness")) %>% select(kobo_farmer_id,country,indicator,subindicator,name_choice) %>% unique() %>%
   dcast(kobo_farmer_id+country+indicator~subindicator,value.var="name_choice")

temp_kpi_calc3 <- d %>% filter(theme=="environmental") %>%
  filter(subindicator %in% c("abd_practices_cropland","abd_practices_area")) %>% select(kobo_farmer_id,country,indicator,subindicator,name_choice,index) %>% unique() %>%
   dcast(kobo_farmer_id+country+indicator+index~subindicator,value.var="name_choice")

temp_kpi_calc <- temp_kpi_calc1 %>% left_join(temp_kpi_calc2) %>% left_join(temp_kpi_calc3) %>%
  mutate(abd_crop_name= ifelse(kobo_farmer_id == 273955054 & abd_crop_name=="None","Groundnut",abd_crop_name))

# Calculate agrobiodiversity concentration score
temp_kpi_calc <- temp_kpi_calc %>%
  mutate_at(c("abd_area_per_crop","abd_crop_area","abd_crop_richness","abd_practices_area"), ~as.numeric(.))  %>%
  # correct cases where area covered by the main crops is more than total cropland area on the farm
  group_by_at(c("kobo_farmer_id","country","indicator")) %>%
  mutate(abd_area_per_crop_summed = sum(abd_area_per_crop)) %>% ungroup() %>%
    mutate(abd_concentration = abd_area_per_crop/abd_crop_area) %>%
  mutate(abd_concentration = ifelse(abd_crop_area < abd_area_per_crop_summed,abd_area_per_crop/abd_area_per_crop_summed, abd_area_per_crop/abd_crop_area)) %>%
  # convert to % by summing the individual crop concentration scores per farm
  group_by_at(c("kobo_farmer_id","country")) %>%
  mutate(abd_concentration_sum = sum(abd_concentration)) %>% ungroup() %>%
  mutate(abd_concentration_score = ifelse(abd_concentration_sum<=1, (1 - abd_concentration_sum)*100,0)) 
  
# Calculate crop richness gap
temp_kpi_calc <- temp_kpi_calc %>%
  group_by_at(c("country")) %>%
  mutate(abd_crop_richness_max = max(abd_crop_richness, na.rm=T),
         abd_crop_richness_min = min(abd_crop_richness, na.rm=T),
         abd_crop_richness_med = median (abd_crop_richness, na.rm=T)) %>% ungroup() %>%
  mutate(abd_crop_richness_index_score = (abd_crop_richness - abd_crop_richness_min)/(abd_crop_richness_max-abd_crop_richness_min)*100)

temp_kpi_calc <- temp_kpi_calc %>%
  select(kobo_farmer_id,country,abd_crop_richness_index_score) %>%
  # remove ABD concentration indicator because I am not convinced it is useful
  # #select(kobo_farmer_id,country, abd_concentration_score,abd_crop_richness_gap_score) %>%
  unique() %>%  
  melt(id.vars=c("kobo_farmer_id","country"),variable.name="subindicator",value.name="score") %>%
  mutate(indicator = ifelse(subindicator== "abd_concentration_score", "kpi6a_abd_concentration",
                            ifelse(subindicator == "abd_crop_richness_index_score","kpi6a_abd_crop_richness_index",NA)))

# Add this back into the main dataset
kpi_scores <- kpi_scores %>% full_join(temp_kpi_calc, by = c("kobo_farmer_id", "country", "indicator", "subindicator", "score"), keep=NULL) %>%
  mutate(subindicator_label = ifelse(indicator=="kpi6a_abd_concentration","Crop concentration index (0-100)",subindicator_label),
         subindicator_label = ifelse(indicator=="kpi6a_abd_crop_richness_index","Crop richness index (0-100)",subindicator_label),
         indicator_order = ifelse(indicator =="kpi6a_abd_concentration",6.11,indicator_order),
         indicator_order = ifelse(indicator =="kpi6a_abd_crop_richness_index",6.12,indicator_order)) %>%
    mutate(module = ifelse(indicator %in% c("kpi6a_abd_concentration","kpi6a_abd_crop_richness_index"),"performance kpi",module)) %>% mutate(theme = ifelse(indicator %in% c("kpi6a_abd_concentration","kpi6a_abd_crop_richness_index"),"environmental",theme))

#kpi_histogram(kpi_scores,"kpi6a_abd_concentration")
kpi_histogram(kpi_scores,"kpi6a_abd_crop_richness_index")
#kpi_all_boxplot(kpi_scores)

### Performance KPI6b biodiversity - abd varietal/breed richness ####
#table(d$indicator,d$module)
#temp <- d %>% filter(indicator %in% c("biodiversity_agrobiodiversity"))
#unique(temp$label_question)

area_unit_livestock <- d %>% filter(indicator =="biodiversity_agrobiodiversity") %>% filter(label_question =="What is the area of land used for livestock production in ${_1_4_1_1_calculate}: Land you own:" ) %>% select(kobo_farmer_id, index, label_choice) %>% unique() %>% rename(area_unit = label_choice)
#area_unit_livestock <- area_unit_livestock$label_choice

d <- d %>% 
  # crop species richness
  mutate(subindicator = ifelse(label_question == "In the last 12 months [add country meaning], how many different crops species (including perennial crops) were produced on your farm","abd_crop_richness",subindicator)) %>%
  mutate(subindicator = ifelse(label_question == "What is the total area of land used for growing crops in ${_1_4_1_1_calculate}?", "abd_crop_area",subindicator)) %>%
  # crop variety - local/exotic 
  mutate(subindicator = ifelse(label_question == "Do the crops you grow come from certified quality seeds or locally adapted varieties (e.g. traditional cultivars, landraces)?"   ,"abd_crop_local",subindicator)) %>%
  
  # livestock species richness
    mutate(subindicator = ifelse(label_question== "In the last 12 months [add country meaning], how many different livestock species were produced in your farm?"    , "abd_livestock_richness",subindicator)) %>%
   mutate(subindicator = ifelse(label_question ==  "What is the area of land used for livestock production in ${_1_4_1_1_calculate}: Land you own:" , "abd_livestock_area_owned",subindicator)) %>%
  mutate(subindicator = ifelse(label_question =="What is the area of land used for livestock production in ${_1_4_1_1_calculate}: Share grazing land:","abd_livestock_area_shared",subindicator)) %>%
    # livestock breed - local/exotic  
  mutate(subindicator = ifelse(label_question ==  "Are the livestock you keep exotic or local?"   ,"abd_livestock_local",subindicator)) %>%
  
  # fish richness
  ### RECHECK THIS WHEN A COUNTRY HAS FISH DATA:
  mutate(subindicator = ifelse(label_question== "In the last 12 months [add country meaning], how many different fish species were produced in your farm?"    , "abd_fish_richness",subindicator)) %>%
  mutate(subindicator = ifelse(label_question== "What is the area of land used for fish production in ${_1_4_1_1_calculate}:"  ,"abd_fish_area", subindicator)) %>%
  mutate(subindicator = ifelse(label_question ==  "Are the fish you keep exotic or local?"   ,"abd_fish_local",subindicator)) %>%
  
  # assign scores
  mutate(score = ifelse(subindicator %in% c("abd_crop_richness", "abd_crop_local","abd_crop_area", "abd_livestock_local", "abd_livestock_richness","abd_livestock_area_owned","abd_livestock_area_shared", "abd_fish_richness","abd_fish_area","abd_fish_local"), name_choice,score))

# Assign scores to crop and livestock based on proportion of local 
#temp <- d %>% filter(subindicator %in% c( "abd_crop_local", "abd_livestock_local")) %>% select(subindicator,label_choice,name_choice, score) %>% unique()
#arrange(temp,subindicator,score)

temp_kpi_calc <- d %>% 
  filter(subindicator %in% c( "abd_crop_local", "abd_livestock_local")) %>%
  mutate(score = case_when(subindicator == "abd_crop_local" & label_choice =="Only or mainly locally adapted varieties are grown."~5,
                           subindicator == "abd_crop_local" & label_choice =="Mainly certified seeds and some locally adapted varieties are grown (e.g. traditional cultivars, landraces)."~4,
                           subindicator == "abd_crop_local" & label_choice =="Some certified seeds and some locally adapted varieties are grown (e.g. traditional cultivars, landraces)."~3,
                           subindicator == "abd_crop_local" & label_choice =="Only or mainly certified quality seeds are grown."~2,
                           subindicator == "abd_crop_local" & label_choice =="I don't know, or seeds are neither certified or locally adapted."~1,.default=as.numeric(score))) %>%
  
    mutate(score = case_when(subindicator == "abd_livestock_local" & label_choice =="Only local breeds are kept."~5,
                           subindicator == "abd_livestock_local" & label_choice =="25% are exotic breeds and 75% are local breeds."~4,
                           subindicator == "abd_livestock_local" & label_choice =="Equal numbers of exotic breeds and local breeds are kept"~3,
                           subindicator == "abd_livestock_local" & label_choice =="75% are exotic breeds and 25% are local breeds."~2,
                           subindicator == "abd_livestock_local" & label_choice =="Only exotic breeds are kept."~1,
                           subindicator == "abd_livestock_local" & label_choice =="No exotic or local breeds are kept."~NA,.default=as.numeric(score))) 
  

temp_kpi_calc <- temp_kpi_calc %>%
 dcast(kobo_farmer_id+country+indicator ~subindicator,value.var="score") %>%
  mutate_at(c( "abd_crop_local","abd_livestock_local"), ~as.numeric(.)) %>%
  group_by_at(c("kobo_farmer_id","country")) %>%
  #rowwise() %>%
  mutate(score = median(c_across(c("abd_crop_local","abd_livestock_local")),na.rm=TRUE)) %>% ungroup() %>%
  mutate(indicator = "kpi6b_abd_variety_diversity",
         subindicator = "abd_variety_breed_diversity",
         subindicator_label = "Use of local varieties and breeds from 1 (only exotic varieties/breeds) to 5 (only local varieties/breeds)") %>%
  select(c("kobo_farmer_id","country","indicator","subindicator","subindicator_label","score"))

kpi_scores <- kpi_scores %>% full_join(temp_kpi_calc, keep=NULL) %>%
  mutate(indicator_order = ifelse(indicator =="kpi6b_abd_variety_diversity",6.2,indicator_order)) %>%
    mutate(module = ifelse(indicator == "kpi6b_abd_variety_diversity","performance kpi",module)) %>% mutate(theme = ifelse(indicator %in% c("kpi6b_abd_variety_diversity"),"environmental",theme))

kpi_histogram(kpi_scores,"kpi6b_abd_variety_diversity")
#kpi_all_boxplot(kpi_scores)

### Performance KPI7 biodiversity - landscape complexity ####
#table(d$indicator,d$module)
#temp <- d %>% filter(indicator %in% c("landscape_complexity","biodiversity_cover"))
#unique(temp$label_question)

d <- d %>%
  # landscape complexity
  mutate(subindicator = ifelse(grepl("How much land area is covered by natural and semi-natural vegetation on land owned, rented or used by the household: Any natural",label_question), "landscape_complexity",subindicator)) %>%
  
  # plant diversity in landscape features
  mutate(subindicator = ifelse(label_question %in% 
                                 c("How would you describe the plant diversity (i.e., number of plant species) in: Bushland patches", 
                                   "How would you describe the plant diversity (i.e., number of plant species) in: Fallow land which is unproductive for at least 1 year", 
                                   "How would you describe the plant diversity (i.e., number of plant species) in: Hedgerows/Live fences", 
                                   "How would you describe the plant diversity (i.e., number of plant species) in: Natural grassland",  
                                   "How would you describe the plant diversity (i.e., number of plant species) in: Remnant forest patches",
                                   "How would you describe the plant diversity (i.e., number of plant species) in: Wetlands", 
                                   "How would you describe the plant diversity (i.e., number of plant species) in: Woodlots"),
                               "landscape_diversity_by_feature",subindicator))

# assign scores
#temp <- d %>% filter(subindicator %in% c( "landscape_complexity", "landscape_diversity_by_feature")) %>% select(subindicator,label_choice,name_choice, score) %>% unique()
#arrange(temp,subindicator,score)

temp_kpi_calc <- d  %>% filter(subindicator %in% c( "landscape_complexity", "landscape_diversity_by_feature")) %>%
  mutate(score = case_when(subindicator == "landscape_complexity" & label_choice =="51-100%"~5,
                           subindicator == "landscape_complexity" & label_choice =="21-50%"~4,
                           subindicator == "landscape_complexity" & label_choice =="11-20%"~3,
                           subindicator == "landscape_complexity" & label_choice =="1-10%"~2,
                           subindicator == "landscape_complexity" & label_choice =="No presence or occurrence."~1,.default=as.numeric(score))) %>%
  
  mutate(score = case_when(subindicator == "landscape_diversity_by_feature" & name_choice %in% c("high")~5,
                           subindicator == "landscape_diversity_by_feature" & name_choice %in% c("medium")~3.67,
                           subindicator == "landscape_diversity_by_feature" & name_choice %in% c("low")~2.34,
                           subindicator == "landscape_diversity_by_feature" & name_choice %in% c("none")~NA, .default=as.numeric(score)))

temp_kpi_calc <- temp_kpi_calc %>% filter(!(module=="agroecology")) %>%
   #filter(subindicator %in% c( "landscape_diversity_by_feature")) %>%
  group_by(kobo_farmer_id,country,subindicator) %>%
  summarise(score = median(score,na.rm=TRUE)) %>%
  dcast(kobo_farmer_id+country~subindicator,value.var="score") %>%
  group_by(kobo_farmer_id, country,landscape_complexity,landscape_diversity_by_feature) %>%
  mutate(score_med = median(landscape_complexity, landscape_diversity_by_feature, na.rm=TRUE)) %>%
  mutate(score = ifelse(landscape_complexity==1,1,
                        ifelse(is.na(landscape_diversity_by_feature), landscape_complexity, score_med)))

temp_kpi_calc <- temp_kpi_calc %>% #filter(subindicator=="landscape_diversity_by_feature") %>%
  mutate(score = as.numeric(score)) %>%
  group_by_at(c("kobo_farmer_id","country")) %>%
  mutate(score = median(score,na.rm=TRUE)) %>% ungroup() %>%
  mutate(indicator = "kpi7_landscape_complexity",
         subindicator = "landscape_complexity",
         subindicator_label = "Proportion and diversity of natural features in the landscape from 1 (no natural features) to 5 (>50% natural features with functionally diverse plant species)") %>%
  select(c("kobo_farmer_id","country","indicator","subindicator","subindicator_label","score")) %>% unique()

kpi_scores <- kpi_scores %>% full_join(temp_kpi_calc, keep=NULL) %>%
  mutate(indicator_order = ifelse(indicator =="kpi7_landscape_complexity", 7, indicator_order)) %>%
    mutate(module = ifelse(indicator == "kpi7_landscape_complexity","performance kpi",module)) %>% mutate(theme = ifelse(indicator %in% c("kpi7_landscape_complexity"),"environmental",theme))

kpi_histogram(kpi_scores,"kpi7_landscape_complexity")
#kpi_all_boxplot(kpi_scores)

### Performance KPI8 climate mitigation ####
sort(unique(d$indicator))
temp <- d %>% filter(indicator %in% c("biodiversity_climate_mitigation") | subindicator %in% c("abd_practices_cropland","abd_practices_area"))
table(temp$subindicator)
sort(unique(temp$label_question))
table(temp$indicator,temp$label_question)
table(temp$label_choice)

d <- d %>%
  mutate(subindicator = ifelse(label_question %in% c("Since when has your household been farming this land?"),"land_use_history",subindicator)) %>%
  mutate(subindicator = ifelse(label_question %in% c("What was the main previous land cover?"),"land_use_previous",subindicator))

temp_kpi_calc <- d %>% filter(theme=="environmental") %>%
  filter(subindicator %in% c("abd_practices_cropland","abd_practices_area")) %>% select(kobo_farmer_id,country,indicator,subindicator,name_choice,index) %>% unique() %>%
  dcast(kobo_farmer_id+country+indicator+index~subindicator,value.var="name_choice") %>%
  mutate(abd_practices_area = as.numeric(abd_practices_area)) %>%
  filter(!is.na(abd_practices_cropland)) %>%
  group_by(kobo_farmer_id) %>% mutate(abd_practices_area_total = sum(abd_practices_area)) %>% ungroup()  %>%
  group_by(kobo_farmer_id, abd_practices_cropland) %>% mutate(abd_practices_cropland_count = n()) %>% ungroup() %>%
  mutate(abd_practices_area = ifelse(abd_practices_cropland =="None", 0, abd_practices_area)) %>% 
  mutate(abd_practices_area_total = ifelse(abd_practices_cropland =="None", 0, abd_practices_area_total)) %>% 
  mutate(abd_practices_area = ifelse(abd_practices_area ==0 & abd_practices_area_total>0, abd_practices_area_total/abd_practices_cropland_count, abd_practices_area)) %>% 
  ungroup() %>%
  # recompute total area incase sum of parts now exceeds total
  group_by(kobo_farmer_id) %>% mutate(abd_practices_area_total = sum(abd_practices_area)) %>% ungroup()  %>%
  mutate(practice_share = abd_practices_area/abd_practices_area_total)

sort(unique(temp_kpi_calc$abd_practices_cropland))
sort(unique(ref_values_cc$Practice))

# Classify practices in the survey into the practice groups listed in our climate change reference values sheet
temp_kpi_calc <- temp_kpi_calc %>%
  mutate(practice_cc_group = case_when(abd_practices_cropland %in% c("Agroforestry","Homegarden","Mango and banana plantation" )~"Agroforestry",
                                       abd_practices_cropland %in% c("Cover crops","legume cultivation")~"Green manure",
                                       abd_practices_cropland %in% c("Mulching")~"Mulching",
                                       abd_practices_cropland %in% c("Crop rotation")~"Crop rotation",
                                       abd_practices_cropland %in% c("Hedgerows/Live fences")~"Embedded natural (hedgerows)",
                                       abd_practices_cropland %in% c("Grass strips", "Fallow (leave land unproductive)","Natural strips/vegetation","Pollinator/Flower strips") ~ "Embedded natural (herbaceous/undefined)",
                                       abd_practices_cropland %in% c("Intercropping","Pull-push","Crop planted around a plot (e.g. Bissap planted around a plot of millet)","Crop planted around a plot of another crop or pasture","Association de culture" )~"Intercropping",
                                       abd_practices_cropland %in% c("Land clearing for agriculture","Burning crop residues")~"Vegetation clearance",
                                       abd_practices_cropland %in% c("Monoculture with perennial crops")~"Monocultures perennial",
                                       abd_practices_cropland %in% c("Monoculture with annual crops","Terracing","Seulement des olives")~"Monocultures annual",
                                       abd_practices_cropland %in% c("None")~ "None", .default="Check")) 

# check that all practices in the dataset have been assigned to a practice group
temp_kpi_calc %>% filter(practice_cc_group == "Check") %>% select(abd_practices_cropland) %>% unique()

# Append climate mitigation scores associated with each practice
temp_kpi_calc <- temp_kpi_calc %>%
  left_join(ref_values_cc,by=c("practice_cc_group"="Practice"))

# Calculate a weighted average
temp_kpi_calc <- temp_kpi_calc %>% 
  mutate(weighted_cc_score = score_overall*practice_share)%>%
  mutate(weighted_cc_score = ifelse(is.nan(weighted_cc_score),NA,weighted_cc_score)) %>%
  group_by(kobo_farmer_id,country) %>%
  summarise(score = sum(weighted_cc_score))

# set indicator names
temp_kpi_calc <- temp_kpi_calc %>%
  mutate(indicator = "kpi8_climate_mitigation",
         subindicator = "climate_mitigation",
         subindicator_label = "Climate mitigation score from 1 to 5, where 1 represents a farm with high GHG emitting and low carbon sequestrating practices, and 5 a farm with low emitting and high sequestrating practices",
         score = ifelse(is.nan(score),NA,score)) 

kpi_scores <- kpi_scores %>% full_join(temp_kpi_calc, keep=NULL) %>%
  mutate(indicator_order = ifelse(indicator =="kpi8_climate_mitigation", 8, indicator_order)) %>%
  mutate(module = ifelse(indicator == "kpi8_climate_mitigation","performance kpi",module)) %>% mutate(theme = ifelse(indicator %in% c("kpi8_climate_mitigation"),"environmental",theme))

kpi_histogram(kpi_scores,"kpi8_climate_mitigation")
#kpi_all_boxplot(kpi_scores)

### Performance KPI9 water use ####
#sort(unique(d$indicator))
#temp <- d %>% filter(indicator =="water" )
#table(temp$name_question)
#table(temp$label_question)
#table(temp$name_choice)
#table(temp$label_choice)

d <- d %>% 
  # months with water stress
  mutate(subindicator = ifelse(label_question %in% c("During which months of the year do you find it difficult to access enough water for your agricultural needs (e.g. growing crops, drinking water for livestock): During a normal year"),"water_stress_normal",subindicator)) %>%
  
  # months of potential irrigition water stress
    mutate(subindicator = ifelse(label_question %in% c("Specify the number of seasons in which cropland is irrigated:"), "water_use_irrigation_seasons", subindicator)) %>%
  mutate(subindicator = ifelse(label_question %in% c("Select the months in wich cropland is irrigated during this season"), "water_use_irrigation_months", subindicator))

temp_kpi_calc <- d %>% filter(subindicator %in% c("water_use_irrigation_months","water_stress_normal"))  %>%
  dcast(kobo_farmer_id+country+module+theme+label_choice~subindicator,value.var="name_choice",length) %>% 
  mutate(irrigation_water_stress = ifelse(water_use_irrigation_months ==1 & water_stress_normal == 1, 1, NA)) %>%
  group_by(kobo_farmer_id, country, module, theme) %>%
  mutate(water_use_irrigation_months_annual = sum(water_use_irrigation_months,na.rm=TRUE),
         irrigation_water_stress_annual = sum(irrigation_water_stress, na.rm=TRUE)) %>%
  mutate(ag_water_stress_annual = sum(water_stress_normal,na.rm=TRUE)) %>%
  ungroup() %>%
  mutate(avoided_irrigation_water_stress =(1-(irrigation_water_stress_annual/water_use_irrigation_months_annual))*100,
         avoided_ag_water_stress = (1 - (ag_water_stress_annual/12))*100) %>%
  mutate(avoided_irrigation_water_stress = ifelse(avoided_irrigation_water_stress == "NaN",NA,avoided_irrigation_water_stress))

temp_kpi_calc1 <- temp_kpi_calc %>% select(kobo_farmer_id,country,module,theme, avoided_ag_water_stress) %>% unique() %>% 
  melt(id.vars=c("kobo_farmer_id","country","module","theme"),variable.name="indicator",value.name="score") %>%
  mutate(indicator =  "kpi9_avoided_ag_water_stress",
         subindicator = "avoided_ag_water_stress",
         subindicator_label = "Share of months WITHOUT agricultural water stress in a normal year (%)",
         indicator_order = 9.1)

temp_kpi_calc2 <- temp_kpi_calc %>% select(kobo_farmer_id,country,module,theme,avoided_irrigation_water_stress) %>% unique() %>% 
  melt(id.vars=c("kobo_farmer_id","country","module","theme"),variable.name="indicator",value.name="score") %>%
  mutate(indicator =  "kpi9b_avoided_irrigation_water_stress",
         subindicator = "avoided_irrigation_water_stress",
         subindicator_label = "Share of months WITHOUT irrigation water stress in a normal year (%), for those months when cropland is irrigated",
         indicator_order = 9.2)

kpi_scores <- kpi_scores %>% full_join(temp_kpi_calc1, keep=NULL) %>% full_join(temp_kpi_calc2, keep=NULL) %>%
    mutate(module = ifelse(indicator %in% c("kpi9_avoided_ag_water_stress","kpi9b_avoided_irrigation_water_stress"),"performance kpi",module)) %>% mutate(theme = ifelse(indicator %in% c("kpi9_avoided_water_stress","kpi9b_avoided_irrigation_water_stress"),"environmental",theme))

kpi_histogram(kpi_scores,"kpi9_avoided_ag_water_stress")
kpi_histogram(kpi_scores,"kpi9b_avoided_irrigation_water_stress")
#kpi_all_boxplot(kpi_scores)

### Performance KPI10 energy use ####
#sort(unique(d$indicator))
#temp <- d %>% filter(indicator =="energy" )
#table(temp$name_question)
#table(temp$label_question)
#table(temp$name_choice)
#table(temp$label_choice)

d <- d %>% 
  mutate(subindicator = ifelse(indicator=="energy" & label_question == "Where do you source most of your energy?", "energy_source", subindicator)) %>%
  mutate(score = ifelse(subindicator %in% c("energy_source"), name_choice, score)) %>% mutate(score = as.numeric(score)) 

# Check what 'other' energy sources were listed
#temp <- d %>% filter(indicator =="energy" ) %>% filter(label_choice =="other")
#sort(unique(temp$label_choice))

temp_kpi_calc <- d %>% select(-theme) %>% filter(indicator == "energy") %>% filter(!(subindicator =="energy_source")) %>% unique() %>%
  mutate(energy_type = case_when(label_choice %in% 
                                   c("Animal traction", 
                                     "Burning plant materials",       
                                     "Human power/by hand only",
                                     "Solar panel") ~ "Renewable",
                                 label_choice %in% 
                                   c("Electricity (national grid)",
                                     "Gas LPG" ,
                                     "Biogas" ,
                                     "Gas",
                                     "Petrol or diesel")~"Non_renewable", 
                                 label_choice %in% c("other") & 
                                   name_choice %in% c("Human power",
                                                      "Water from underground") ~ "Renewable", .default=label_choice))

# Get count of renewable and non-renewable energy sources
temp_kpi_calc <-temp_kpi_calc %>%
  dcast(kobo_farmer_id+country~energy_type,value.var="energy_type",fun=length) 

# Score based on share of renewable
temp_kpi_calc <-temp_kpi_calc %>%
  mutate(energy_type_score = ifelse(Renewable>0 & Non_renewable<1,5,
                       ifelse(Renewable>0 & Non_renewable>0, 3,
                              ifelse(Renewable<1 & Non_renewable>0, 1, NA)))) %>%
  mutate(energy_type_score = as.numeric(energy_type_score))

# Combine with information on energy production source
temp_kpi_calc <- temp_kpi_calc %>% left_join(
  d %>% filter(subindicator =="energy_source") %>% 
    select(kobo_farmer_id,score) %>%
    rename("energy_source_score" = score))

temp_kpi_calc <- temp_kpi_calc %>%
  group_by(kobo_farmer_id,country,energy_type_score,energy_source_score) %>%
  mutate(score = median(c(energy_type_score,energy_source_score),na.rm=T)) %>% ungroup() %>%
  select(kobo_farmer_id,country,score) %>%
  mutate(indicator = "kpi10_energy_use",
         subindicator = "energy_use_sustainability",
         subindicator_label = "Sustainability of energy use with scores from 1 (Non-renewable and externally produced) to 5 (Renewable and self-produced)",
         indicator_order = 10)

kpi_scores <- kpi_scores %>% full_join(temp_kpi_calc) %>%
  mutate(module = ifelse(indicator %in% c("kpi10_energy_use"),"performance kpi",module))  %>% mutate(theme = ifelse(indicator %in% c("kpi10_energy_use"),"environmental",theme))

kpi_histogram(kpi_scores,"kpi10_energy_use")
#kpi_all_boxplot(kpi_scores)

### Performance KPI11 income ####
#sort(unique(d$indicator))
#temp <- d %>% filter(indicator =="income")
#sort(unique(temp$label_question))

# set reference national annual income (local currency per year) used as the benchmark to determine how household incomes compare to this
# default is to use the MEAN income recorded in the country-specific HOLPA survey data 
# alternative is to use country-sourced data: activate this option only if information on income is provided in ref_values_country
ref_income <- ref_values_country %>%
  select(income_ref_clean) 
ref_income <- ref_income$income_ref_clean[1]
#ref_income <- NA

d <- d %>%
  mutate(subindicator = case_when(grepl("In the past 12 months, approximately how much income", label_question)~"income_amount",
                                  grepl("Does the household earn enough income",label_question)~"income_sufficiency", 
         grepl("How would you rate the stability of the household income?",label_question) ~ "income_stability",
         grepl("In the last 12 months, did the household spend more",label_question)~"income_versus_expenditures",
                                  .default=subindicator)) 

temp_kpi_calc <- d %>% filter(subindicator =="income_amount") %>%
  mutate(score = ifelse(name_choice %in% c("9999","nd"),NA,name_choice)) %>%
  mutate(score = as.numeric(score)) %>%
  filter(!(is.na(score)))  %>%
  group_by(kobo_farmer_id,country) %>%
  summarise(income=sum(score,na.rm=TRUE),
            income_sources = n()) %>%
  group_by(country) %>%
  mutate(mean_income = mean(income,na.rm=T)) %>%
  mutate(ref_income = ifelse(!is.na(ref_income),ref_income,mean_income)) %>%
  mutate(score = income/ref_income)

temp_kpi_calc <- temp_kpi_calc %>%
  select(kobo_farmer_id,country,score) %>%
  mutate(indicator = "kpi11_hh_income_v_mean",
       subindicator = "hh_income_compared_to_average",
       subindicator_label = "Ratio of household income compared to the average",
       indicator_order = 11.1)

kpi_scores <- kpi_scores %>% full_join(temp_kpi_calc, keep=NULL) %>%
  mutate(module = ifelse(indicator %in% c("kpi11_hh_income_v_mean"),"performance kpi",module)) %>%
  mutate(theme = ifelse(indicator %in% c("kpi11_hh_income_v_mean"),"economic",theme)) 

kpi_histogram(kpi_scores,"kpi11_hh_income_v_mean")
#kpi_all_boxplot(kpi_scores)

### Performance KPI11b income stability ####
temp_kpi_calc <- d %>% filter(subindicator =="income_stability") %>% select(-module,-index, -theme) %>%unique()

#table(temp_kpi_calc$label_choice,temp_kpi_calc$name_choice)
temp_kpi_calc <- temp_kpi_calc %>%
  mutate(score = ifelse(name_choice %in% c("9999","nd"),NA,name_choice)) %>%
  mutate(score = as.numeric(score)) %>%
  filter(!(is.na(score)))

temp_kpi_calc <- temp_kpi_calc %>%
  select(kobo_farmer_id,country,score) %>%
  mutate(indicator = "kpi11b_hh_income_stability",
       subindicator = "hh_income_stability",
       subindicator_label = "Income stability from 1 (income declining) to 5 (income increasing)",
       indicator_order = 11.2)

kpi_scores <- kpi_scores %>% full_join(temp_kpi_calc, keep=NULL) %>%
  mutate(module = ifelse(indicator %in% c("kpi11b_hh_income_stability"),"performance kpi",module)) %>%
  mutate(theme = ifelse(indicator %in% c("kpi11b_hh_income_stability"),"economic",theme)) 

kpi_histogram(kpi_scores,"kpi11b_hh_income_stability")
#kpi_all_boxplot(kpi_scores)

### Performance KPI11c income-expenditures ####
temp_kpi_calc <- d %>% filter(subindicator =="income_versus_expenditures") %>% select(-module,-index, -theme) %>%unique()

#table(temp_kpi_calc$label_choice,temp_kpi_calc$name_choice)

temp_kpi_calc <- temp_kpi_calc %>%
  mutate(score = ifelse(name_choice %in% c("2","nd","-9999"),NA,
                        ifelse(name_choice %in% c("0"), "1", # no, did not spend more money than earned
                               ifelse(name_choice %in% ("1"), "0", name_choice)))) %>% # yes, spent more money than earned
  mutate(score = as.numeric(score)) %>%
  filter(!(is.na(score)))

temp_kpi_calc <- temp_kpi_calc %>%
  select(kobo_farmer_id,country,score) %>%
  mutate(indicator = "kpi11c_hh_income_v_expenditures",
       subindicator = "hh_income_v_expenditure",
       subindicator_label = "Income higher than expenditures (yes=1,no=0)",
       indicator_order = 11.3)

kpi_scores <- kpi_scores %>% full_join(temp_kpi_calc, keep=NULL) %>%
  mutate(module = ifelse(indicator %in% c("kpi11c_hh_income_v_expenditures"),"performance kpi",module)) %>%
  mutate(theme = ifelse(indicator %in% c("kpi11c_hh_income_v_expenditures"),"economic",theme)) 

kpi_histogram(kpi_scores,"kpi11c_hh_income_v_expenditures")
#kpi_all_boxplot(kpi_scores)

### Performance KPI11d income sufficiency ####

temp_kpi_calc <- d %>% filter(subindicator =="income_sufficiency") %>% select(-module,-index, -theme) %>%unique()
#table(temp_kpi_calc$label_choice,temp_kpi_calc$name_choice)

temp_kpi_calc <- temp_kpi_calc %>%
  mutate(score = ifelse(name_choice %in% c("nd","-9999"),NA,name_choice)) %>%
  mutate(score = as.numeric(score)) %>%
  filter(!(is.na(score)))

temp_kpi_calc <- temp_kpi_calc %>%
  select(kobo_farmer_id,country,score) %>%
  mutate(indicator = "kpi11d_hh_income_sufficiency",
       subindicator = "hh_income_sufficiency",
       subindicator_label = "Income sufficiency from 1 (insufficient) to 5 (sufficient)",
       indicator_order = 11.4)

kpi_scores <- kpi_scores %>% full_join(temp_kpi_calc, keep=NULL) %>%
  mutate(module = ifelse(indicator %in% c("kpi11d_hh_income_sufficiency"),"performance kpi",module)) %>%
  mutate(theme = ifelse(indicator %in% c("kpi11d_hh_income_sufficiency"),"economic",theme)) 

kpi_histogram(kpi_scores,"kpi11d_hh_income_sufficiency")
#kpi_all_boxplot(kpi_scores)

### Performance KPI12 yield gap ####

#sort(unique(d$indicator))
#temp <- d %>% filter(indicator =="productivity_crops" | name_question %in% c("_3_4_3_1_3_calculate"))

#print(temp %>% select(name_question_recla, label_question) %>% unique(), n=50)
#print(temp %>% select(name_question, label_question) %>% unique(), n=50)

area_unit_productivity <- d %>% filter(subindicator =="abd_area_per_crop") %>% select(kobo_farmer_id, label_choice) %>% unique() %>% rename(area_unit = label_choice)

temp_kpi_calc <- d %>% filter(indicator %in%c("productivity_crops") | name_question %in% c("_3_4_3_1_3_calculate","_3_3_2_1_5_9_1") | subindicator %in% c("abd_crop_name", "abd_area_per_crop","abd_crop_area")) %>%
  mutate(subindicator = 
           case_when(name_question %in% c("_3_4_2_1_5_1_calculate")~  "production_unit",
                     name_question %in% c("_3_4_2_1_5_2")~ "production_total",

                          # production end-use
                     name_question %in% c("_3_4_2_1_6_1/human_consumption")~ "production_use_consumption_human", 
                     name_question %in% c("_3_4_2_1_6_1/livestock_consumption")~ "production_use_own_livestock", 
                      name_question %in% c("_3_4_2_1_6_1/consumer")~ "production_use_sold_direct", 
                     name_question %in% c("_3_4_2_1_6_1/cooperative")~ "production_use_sold_cooperative)", 
                     name_question %in% c("_3_4_2_1_6_1/market_place")~ "production_use_sold_market", 
                     name_question %in% c("_3_4_2_1_6_1/trader_supermarket")~ "production_use_sold_trader", 
                     name_question %in% c("_3_4_2_1_6_1/gifts")~ "production_use_gift)", 
                     name_question %in% c("_3_4_2_1_6_1/waste/losses")~ "production_use_waste", 
                     name_question %in% c("_3_4_2_1_6_1/other")~ "production_use_other)", 
                     
                     # production end-use quantity
                     name_question %in% c("_3_4_2_1_6_2_1")~ "production_use_consumption_human_quan",
                     name_question %in% c("_3_4_2_1_6_2_2")~ "production_use_own_livestock_quan",
                     name_question %in% c("_3_4_2_1_6_2_3")~ "production_use_sold_direct_quan",
                     name_question %in% c("_3_4_2_1_6_2_4")~ "production_use_sold_cooperative_quan",
                     name_question %in% c("_3_4_2_1_6_2_5")~ "production_use_sold_market_quan",
                     name_question %in% c("_3_4_2_1_6_2_6")~ "production_use_sold_trader_quan",
                     name_question %in% c("_3_4_2_1_6_2_7")~ "production_use_gift_quan)",
                     name_question %in% c("_3_4_2_1_6_2_8")~ "production_use_waste)",
                     name_question %in% c("_3_4_2_1_6_1_1")~ "production_use_other",
                     .default = subindicator)) 

# format crop names and production units
if(country %in% c("laos","kenya","senegal","zimbabwe")){
  ref_values_country <- ref_values_country %>%
    rename(crops_names = main_crops_common_names)
}

ref_values_country <- ref_values_country %>% mutate(crops_names = ifelse(crops_names %in% c( "Maize", "Maize ", "maize"),"Corn",crops_names))

if(country=="peru"){
  ref_values_country <- ref_values_country %>%
    # remove spanish// in production unit column
    mutate(`production unit` = sub("(.*)//*","",`production unit`))
}

# total cropland area
temp_kpi_calc1 <- temp_kpi_calc %>%
  filter(subindicator %in% c("abd_crop_area")) %>%
  select(kobo_farmer_id,subindicator,name_choice) %>% unique() %>%
  dcast(kobo_farmer_id ~ subindicator,value.var = "name_choice") 

# production and area per crop
temp_kpi_calc2 <- temp_kpi_calc  %>%
  left_join(area_unit_productivity) %>%
  filter(subindicator %in% c("abd_crop_name","production_total","production_unit","abd_area_per_crop", "area_unit","area_unit_productivity")) %>%
  select(kobo_farmer_id,country,index,subindicator,name_choice) %>% unique() %>%
  dcast(kobo_farmer_id+country+index ~ subindicator,value.var = "name_choice") %>%
  left_join(area_unit_productivity) %>%
  left_join(temp_kpi_calc1)

temp_kpi_calc2 %>% select(abd_crop_name, production_unit) %>% unique()

temp_kpi_calc2 <- temp_kpi_calc2 %>% 
  mutate(abd_crop_name = str_to_sentence(abd_crop_name)) %>%
  mutate(abd_crop_name = ifelse(abd_crop_name == "Maize","Corn",abd_crop_name)) %>%
  mutate(abd_crop_name= ifelse(kobo_farmer_id == 273955054 & abd_crop_name=="None", "Groundnut", abd_crop_name)) %>%
  left_join(ref_values_country %>% rename(production_unit =`production unit`) %>%
              mutate(crops_names = str_to_sentence(crops_names)) %>%
              select(crops_names, production_unit, yield_conversion_unit_to_kg) %>% unique(),by=c("abd_crop_name"="crops_names","production_unit" = "production_unit")) %>%
  mutate_at(c("abd_area_per_crop","production_total","abd_crop_area", "yield_conversion_unit_to_kg"),~as.numeric(.)) %>%
  mutate(yield_conversion_unit_to_kg = case_when(production_unit %in% c("Kilograms","kilograms", "kg","Kg", "Kgs","kgs", "Kilogrammes","kilogrammes")~1,
                                                 production_unit %in% c("Lorry 6tonnes" )~6000,
                                                 production_unit %in% c("tonnes", "Tonnes","tons","Tons")~1000,
                                                 production_unit %in% c("150kg bags" )~150,
                                                 production_unit %in% c("120kg bag")~120,
                                                 production_unit %in% c("110Kg bag")~110,
                                                 production_unit %in% c("100Kg bag","100Kg bag" ,"100th bag")~100,
                                                 production_unit %in% c("90kg bag")~90,
                                                 production_unit %in% c("70kg bag")~70,
                                                 production_unit %in% c("60kg bag")~60,
                                                production_unit %in% c("50kg bag")~50,
                                                production_unit %in% c("25kg bag")~25,
                                                production_unit %in% c("20kg bucket")~20,
                                                production_unit %in% c("10kg bucket")~10,
                                                .default=yield_conversion_unit_to_kg))


temp_kpi_calc2 <- temp_kpi_calc2 %>%
  mutate_at(vars(abd_area_per_crop, production_total,yield_conversion_unit_to_kg ),as.numeric) %>%
  # check if the area for the three main crops is > total farm cropland area
  # don't remove these but note that these farms must have multicrop systems, or area errors
  group_by(kobo_farmer_id) %>% mutate(abd_area_per_crop_summed = sum(abd_area_per_crop)) %>% ungroup() %>%
  mutate(abd_area_per_crop_gt_abd_crop_area = ifelse(abd_area_per_crop_summed> abd_crop_area,1,0)) %>%
  
  # calculate kg/ha production 
  mutate(production_total_kg = production_total*yield_conversion_unit_to_kg,
         production_area_ha = ifelse(area_unit %in% c("acre","Acre","acres","Acres"),abd_area_per_crop*acre_to_hectare, abd_area_per_crop)) %>%
  mutate(production_kg_ha = production_total_kg/production_area_ha )

# Now calculate yield gap, based on locally attainable yields

temp_kpi_calc3 <- temp_kpi_calc2 %>% select(-index) %>%
  left_join(ref_values_country %>%
              mutate(crops_names = str_to_sentence(crops_names)) %>%
              select(crops_names, yield_ref_rainfed_clean) %>% filter(!is.na(yield_ref_rainfed_clean)) %>%  unique(), by=c("abd_crop_name" = "crops_names"), relationship = "many-to-many") %>%
  mutate(production_kg_ha = ifelse(is.infinite(production_kg_ha),0, production_kg_ha)) %>%
  mutate(yield_ref_rainfed_clean = as.numeric(yield_ref_rainfed_clean)) %>%
  mutate(yield_to_ref_ratio = production_kg_ha/yield_ref_rainfed_clean) %>%
  mutate(yield_gap = ifelse(yield_to_ref_ratio>1 , 0, 
                            ifelse(yield_to_ref_ratio == 0, NA, (1- yield_to_ref_ratio)*100))) %>% filter(!is.na(yield_gap))

temp_kpi_calc <- temp_kpi_calc3 %>%
  group_by(kobo_farmer_id,country) %>%
  summarise(score = mean(yield_gap, na.rm=TRUE)) %>%
  mutate(indicator = "kpi12_yield_gap",
       subindicator = "yield_gap",
       subindicator_label = "Yield gap from 0% (no gap) to 99% (yields at 1% of potential)",
       indicator_order = 12)

kpi_scores <- kpi_scores %>% full_join(temp_kpi_calc, keep=NULL) %>%
  mutate(module = ifelse(indicator %in% c("kpi12_yield_gap"),"performance kpi",module)) %>%
  mutate(theme = ifelse(indicator %in% c("kpi12_yield_gap"),"economic",theme)) 

kpi_histogram(kpi_scores,"kpi12_yield_gap")
#kpi_all_boxplot(kpi_scores)

### Performance KPI13 labour productivity ####
#sort(unique(d$indicator))
#temp <- d %>% filter(indicator =="labour_productivity")
#sort(unique(temp$label_question))
#table(temp$label_question,temp$name_question_recla)

temp_kpi_calc <- d %>% filter(indicator =="labour_productivity") %>%
  mutate(subindicator = case_when(label_question %in% c("Number of household members working PERMANENTLY (all year around) on your farm")  | name_question_recla == "_3_4_1_1_7_1_calculate" ~ "labour_number_workers_hh_perm", # responses in name_choice in various formats needs sorting, e.g. 1 Male adults (18 and 65 years old), Male adults (18 and 65 years old), 2 Male adults (18 and 65 years old)
                                  
                                   label_question %in% c("Number of household members working  SEASONALY (only during peak period) on your farm")  | name_question_recla == "_3_4_1_1_7_2_calculate" ~ "labour_number_workers_hh_peakseas", # responses in name_choice in various formats needs sorting, e.g. 1 Male adults (18 and 65 years old), Male adults (18 and 65 years old), 2 Male adults (18 and 65 years old)
                                  
                                  label_question %in% c("Number of ${_3_4_1_2_1_1_calculate} that work as PERMANENT hired/free/exchange laborers on your farm")  | name_question_recla == "_3_4_1_2_1_1_1" ~ "labour_number_workers_perm", # responses in name_choice in numeric format (integer)
                                  
                                  label_question %in% c("Number of ${_3_4_1_2_1_2_calculate} that work during SEASON ${_3_4_1_2_1_2_1_calculate}:")  | name_question_recla == "_3_4_1_2_1_2_1_3" ~ "labour_number_workers_seas",  # responses in name_choice in numeric format (integer)
                                  
                                  label_question %in% c("Number of household members working during SEASON ${_3_4_1_2_1_2_1_calculate}:")  | name_question_recla == "_3_4_1_2_7_2_3" ~ "labour_number_workers_hh_seas", # responses in name_choice in numeric format (integer)
                                  
                                   label_question %in% c("Average number of hours worked per day per household member working PERMANENTLY (all year around) on your farm" )  | name_question_recla == "_3_4_1_1_7_1_1" ~ "labour_hours_hh_member_perm", # responses in name_choice in numeric format (integer)
                                  
                                  label_question %in% c("Average number of hours worked per day per household member during SEASON ${_3_4_1_2_1_2_1_calculate}:")  | name_question_recla == "_3_4_1_2_7_2_4" ~ "labour_hours_hh_member_seas", # responses in name_choice in numeric format (integer)
                                  
                                   label_question %in% c("Average number of hours worked per day per labourer by PERMANENT hired/free/exchange laborers on your farm" )  | name_question_recla == "_3_4_1_2_1_1_2" ~ "labour_hours_worker_perm", # responses in name_choice in numeric format (integer)
                                  
                                    label_question %in% c("Average number of hours worked per day per labourer during SEASON ${_3_4_1_2_1_2_1_calculate} by SEASONAL hired/free/exchange laborers on your farm:")  | name_question_recla == "_3_4_1_2_1_2_1_4" ~ "labour_hours_worker_seas", # responses in name_choice in numeric format (integer)
                                  
                                     label_question %in% c("Select the months worked per year for SEASON ${_3_4_1_2_7_2_1_calculate} by household members working SEASONALY")  | name_question_recla == "_3_4_1_2_7_2_2" ~ "labour_work_months_hh_member_seas", # name_choice has months in integer, label_choice has month names (3 letter)
                                  
                                  # the following question is missing for ZIMBABWE:
                                  label_question %in% c("Select the months worked per year for SEASON ${_3_4_1_2_1_2_1_calculate} by SEASONAL hired/free/exchange laborers on your farm:")  | name_question_recla == "_3_4_1_2_1_2_1_2" ~ "labour_work_months_workers_seas", # name_choice has months in integer, label_choice has month names (3 letter)
                                  .default = subindicator))
                                                      
#print(arrange(temp_kpi_calc %>% select(subindicator,name_choice, label_choice,type_question, kobo_farmer_id),kobo_farmer_id),n=80)
#d %>% filter(grepl("Select the months worked per year for SEASON",label_question)) %>% select(label_question) %>% unique()

# Number of PERMANENT workers and hours of activity
temp_kpi_calc1 <- temp_kpi_calc %>% filter(subindicator %in% c("labour_number_workers_perm", "labour_hours_worker_perm", "labour_hours_hh_member_perm")) %>%
  dcast(kobo_farmer_id+country+index ~subindicator,value.var="name_choice") %>%
  # add in number of workers from hh based on calculated data
  left_join(temp_kpi_calc %>% filter(subindicator %in% c("labour_number_workers_hh_perm")) %>%
  dcast(kobo_farmer_id+country+index ~subindicator,value.var="name_choice") %>%
  mutate(labour_number_workers_hh_perm_clean =sub("^(\\d+).*", "\\1", labour_number_workers_hh_perm)) %>% select(-labour_number_workers_hh_perm), 
  by=c("kobo_farmer_id","country", "index")) %>%
  mutate(across(-c(kobo_farmer_id,country,index),as.numeric)) %>%
  mutate(across(-c(kobo_farmer_id,country,index), ~ if_else(.x %in% c(9999, 999,-9999,-999,5555), NA_real_, .x)))

temp_kpi_calc1 <- temp_kpi_calc1 %>%
   # assume no days off since we have no infomation on number of unworked days
    mutate(labour_hours_per_year_workers_perm = labour_number_workers_perm * labour_hours_worker_perm * 365,
         labour_hours_per_year_hh_perm = labour_number_workers_hh_perm_clean * labour_hours_hh_member_perm * 365) %>%
  group_by(kobo_farmer_id, country) %>%
  mutate(total_labour_hours_per_year_workers_perm = sum(labour_hours_per_year_workers_perm, na.rm=TRUE),
  total_labour_hours_per_year_hh_perm = sum(labour_hours_per_year_hh_perm, na.rm=TRUE))

# Number of SEASONAL workers and hours of activity
temp_kpi_calc2 <- temp_kpi_calc %>% filter(subindicator %in% c("labour_number_workers_seas", "labour_hours_worker_seas", "labour_number_workers_hh_seas","labour_hours_hh_member_seas")) %>%
  dcast(kobo_farmer_id+index~subindicator,value.var="name_choice") %>% 
  # now need to match season to response....
  left_join(temp_kpi_calc %>% 
              filter(subindicator %in% c("labour_work_months_hh_member_seas","labour_work_months_workers_seas")) %>%
  dcast(kobo_farmer_id+country+index~subindicator,value.var="name_choice", length),
  # %>%rename(labour_number_of_months = "."),
  by=c("kobo_farmer_id","index")) %>%
  mutate(across(-c(kobo_farmer_id,country,index),as.numeric)) %>%
  mutate(across(-c(kobo_farmer_id,country, index), ~ if_else(.x %in% c(9999, 999,-9999,-999,5555), NA_real_, .x)))

if(country %in% c("zimbabwe")){
  temp_kpi_calc2 <- temp_kpi_calc2 %>% 
    mutate(labour_work_months_workers_seas = NA)
}

temp_kpi_calc2 <- temp_kpi_calc2 %>%
  # assume 30 days in every month and no days off since we have no infomation on number of unworked days
  mutate(labour_hours_per_year_workers_seas = labour_number_workers_seas * labour_hours_worker_seas * labour_work_months_workers_seas * 30,
         labour_hours_per_year_hh_seas = labour_number_workers_hh_seas * labour_hours_hh_member_seas * labour_work_months_hh_member_seas * 30) %>%
  group_by(kobo_farmer_id, country) %>%
  mutate(total_labour_hours_per_year_workers_seas = sum(labour_hours_per_year_workers_seas, na.rm=TRUE),
  total_labour_hours_per_year_hh_seas = sum(labour_hours_per_year_hh_seas, na.rm=TRUE))

# combine permanent and seasonal labour hours 
temp_kpi_calc3 <- temp_kpi_calc1 %>% 
  select(kobo_farmer_id,country, total_labour_hours_per_year_workers_perm, total_labour_hours_per_year_hh_perm) %>% unique() %>%
  left_join(temp_kpi_calc2 %>% 
              select(kobo_farmer_id, total_labour_hours_per_year_workers_seas, total_labour_hours_per_year_hh_seas) %>% unique(), 
            by=c("kobo_farmer_id","country")) %>%
  mutate(total_labour_hours_per_year = sum(total_labour_hours_per_year_workers_perm, total_labour_hours_per_year_workers_seas, total_labour_hours_per_year_hh_perm, total_labour_hours_per_year_hh_seas, na.rm=TRUE))

# standardise by agricultural land area 
temp_kpi_calc4 <- d %>% filter(name_question %in% c("_3_4_2_1_1","_3_4_2_2_1_1","_3_4_2_2_1_2", "_3_4_2_3_2" ) | label_question %in% c("What is the total area of land used for growing crops in ${_1_4_1_1_calculate}?", "What is the area of land used for livestock production in ${_1_4_1_1_calculate}: Land you own:", "What is the area of land used for livestock production in ${_1_4_1_1_calculate}: Share grazing land:" , "What is the total surface area in ${_1_4_1_1_calculate} of water bodies, wetlands, paddy fields or other aquaculture systems used for producing fish?" ))  %>% 
  select(kobo_farmer_id, subindicator,name_question, label_question,name_choice)

area_unit_land <- d  %>% filter(name_question %in% c("_3_4_2_1_1","_3_4_2_2_1_1","_3_4_2_2_1_2", "_3_4_2_3_2" ) | label_question %in% c("What is the total area of land used for growing crops in ${_1_4_1_1_calculate}?", "What is the area of land used for livestock production in ${_1_4_1_1_calculate}: Land you own:", "What is the area of land used for livestock production in ${_1_4_1_1_calculate}: Share grazing land:" , "What is the total surface area in ${_1_4_1_1_calculate} of water bodies, wetlands, paddy fields or other aquaculture systems used for producing fish?" )) %>% select(kobo_farmer_id, name_question, label_choice) %>% unique() %>% rename(area_unit = label_choice)

temp_kpi_calc4 <- temp_kpi_calc4 %>% left_join(area_unit_land,by=c("kobo_farmer_id","name_question"))  %>% 
  mutate(name_choice  = as.numeric(name_choice)) %>%
  mutate(area_ha = ifelse(area_unit %in% c("acre","acres","Acre","Acres"), name_choice*acre_to_hectare, name_choice)) %>%
  group_by(kobo_farmer_id) %>% mutate(ag_land_area_ha = sum(area_ha,na.rm=TRUE))

temp_kpi_calc <- temp_kpi_calc3 %>% select(kobo_farmer_id, country, total_labour_hours_per_year) %>%
  full_join(temp_kpi_calc4 %>% select(kobo_farmer_id, ag_land_area_ha) %>% unique()) %>%
    mutate(score = total_labour_hours_per_year/ag_land_area_ha, na.rm=TRUE) %>%
  select(kobo_farmer_id,country,score) %>%
  mutate(indicator = "kpi13a_labour_input",
       subindicator = "labour_input",
       subindicator_label = "Labour in hours/yr/ha agricultural land",
       indicator_order = 13.1)

# calculate agricultural income output in USD per labour input

exchange_rate_to_usd <- ref_values_country %>% select(currency_exchange_local_to_usd) %>% unique() 
exchange_rate_to_usd <- exchange_rate_to_usd$currency_exchange_local_to_usd

temp_kpi_calc5 <- d %>% filter(subindicator =="income_amount") %>%
  mutate(score = ifelse(name_choice %in% c("9999","nd","999","-9999","5555"),NA,name_choice)) %>%
  mutate(score = as.numeric(score)) %>%
  filter(!(is.na(score))) %>%
  filter(label_question %in% c("In the past 12 months, approximately how much income in [local currency] did the household make from: Crop production" ,"In the past 12 months, approximately how much income in [local currency] did the household make from: Livestock production"  ))  %>%
  mutate(income_usd = score*exchange_rate_to_usd) %>%
  group_by(kobo_farmer_id) %>% 
  summarise(income_ag_production = sum(income_usd, na.rm=TRUE)) %>%
  full_join(temp_kpi_calc3 %>% select(kobo_farmer_id, country, total_labour_hours_per_year)) %>%
      mutate(score = income_ag_production/total_labour_hours_per_year) %>%
  select(kobo_farmer_id,country,score) %>%
  mutate(indicator = "kpi13b_labour_productivity",
       subindicator = "income_per_hour_of_labour",
       subindicator_label = "Annual income (USD) from agricultural sources per hour of labour",
       indicator_order = 13.2)

# Add into kpi score dataset
kpi_scores <- kpi_scores %>% full_join(temp_kpi_calc, keep=NULL) %>%
  full_join(temp_kpi_calc5, keep=NULL) %>%
  mutate(module = ifelse(indicator %in% c("kpi13a_labour_input", "kpi13b_labour_productivity"),"performance kpi",module)) %>%
  mutate(theme = ifelse(indicator %in% c("kpi13a_labour_input", "kpi13b_labour_productivity"),"economic",theme)) 

kpi_histogram(kpi_scores,"kpi13a_labour_input")
kpi_histogram(kpi_scores,"kpi13b_labour_productivity")
#kpi_all_boxplot(kpi_scores)

### Performance KPI14 climate resilience ####
#sort(unique(d$indicator))
#temp <- d %>% filter(grepl("climate_resilience", indicator))
#sort(unique(temp$label_question))

# %in% c( "climate_resilience_adaptative_capacity" , "climate_resilience_assets", "climate_resilience_basic_services" , "climate_resilience_shocks", "climate_resilience_social_network"  )

temp_kpi_calc <- d %>% filter(grepl("climate_resilience", indicator)) %>%
  
                              # ABS - Access to basic services pillar
  mutate(subindicator = case_when(grepl("Does your household have the following services", label_question) | name_question %in% c("_4_1_5_1_1","_4_1_5_1_2","_4_1_5_1_3", "_4_1_5_1_4", "_4_1_5_1_5", "_4_1_5_1_6") ~ "ABS_service_in_hh",
                                  
                                  grepl("How far (one way) is the household from", label_question) | name_question %in% c("_4_1_5_2_1" ,"_4_1_5_2_1_1", "_4_1_5_2_1_2", "_4_1_5_2_2","_4_1_5_2_2_1", "_4_1_5_2_2_2", "_4_1_5_2_3", "_4_1_5_2_3_1", "_4_1_5_2_3_2", "_4_1_5_2_4", "_4_1_5_2_4_1", "_4_1_5_2_4_2", "_4_1_5_2_5", "_4_1_5_2_5_1", "_4_1_5_2_5_2", "_4_1_5_2_6", "_4_1_5_2_6_1", "_4_1_5_2_6_2",  "_4_1_5_2_7", "_4_1_5_2_7_1", "_4_1_5_2_7_2") ~ "ABS_service_access",
  
                                  # AST - Assets pillar
                                  grepl("How many of the following assets do household members own?", label_question) | grepl("Other asset (please specify)", label_question) | name_question %in% c("_4_1_4_1","_4_1_4_2","_4_1_4_3","_4_1_4_4", "_4_1_4_5", "_4_1_4_6", "_4_1_4_7", "_4_1_4_8", "_4_1_4_9", "_4_1_4_10", "_4_1_4_11", "_4_1_4_11", "_4_1_4_12", "_4_1_4_13", "_4_1_4_13_1") ~ "AST_assets",
                                  
                                  # SSN - Social safety nets pillar
                                  #  Not used: 
                                  #"Do any children in the household attend school?" 
                                  # NOTE: No question about how many days attended in last 4 weeks...
                                  grepl("On average, how many free schools meals were received per week over the last 4 weeks of schools attendance", label_question) | name_question %in% c("_4_1_6_1_1") ~ "SSN_school_meals",
                                  grepl("Would any of the following individuals or organisations provide your household support", label_question) | name_question %in% c("_4_1_3_2_1","_4_1_3_2_2","_4_1_3_2_3","_4_1_3_2_4","_4_1_3_2_5","_4_1_3_2_6","_4_1_3_2_7", "_4_1_3_2_8","_4_1_3_2_9","_4_1_3_2_10","_4_1_3_2_11","_4_1_3_2_12","_4_1_3_2_13","_4_1_3_2_13_1") ~ "SSN_hh_support",
                                    # AC - Adaptive capacity pillar
                                  grepl("Can you read and write in any language?", label_question) | name_question %in% c("_4_1_1_1") ~ "AC_literacy",
                                  #  Not used: "What is the highest level of school you attended?"
                                  grepl("Please indicate the highest level of school attended by most" , label_question) | name_question %in% c("_4_1_1_2","_4_1_1_3") ~ "AC_highest_school_hh_working_age",
                                   grepl("Training in" , label_question) | label_question == "Other training (please specify)" | name_question %in% c("_4_1_1_4_1","_4_1_1_4_3","_4_1_1_4_4") ~ "AC_training_hh",
                                  label_question %in% c("Please select all the sources of income for your household?","Please specify other source of income"  ) | name_question %in% c("_2_4_1","_2_4_1_2") ~ "AC_income_sources",
                                  label_question %in% c("In the past 7 days, what percentage of the household's income was used for buying food" ) | name_question %in% c("_4_1_2_2") ~ "AC_income_on_food",
                                  label_question %in% c( "In the past 5 years, has your household needed credit to support investment in your farming business, but was unable to obtain it?" ) | name_question %in% c("_4_1_1_5") ~ "AC_access_to_credit",
                                  # not used: "Have your farm/household fully paid off the credit?"  
                                  # note, next question only asked if credit remains unpaid
                                  label_question %in% c( "How do you feel about your farm/household's ability to meet credit repayments now and until the loans are fully repaid?" ) | name_question %in% c("_4_1_1_5_4") ~ "AC_credit_repayments",
                                   label_question %in% c( "Do you have insurance against agricultural losses?"  ) | name_question %in% c("_4_1_1_6") ~ "AC_ag_insurance",
                                   label_question %in% c( "Do you have access to subsidies for agricultural inputs?" , "Can you specify which subsidy?"   ) | name_question %in% c("_4_1_1_7") ~ "AC_ag_subsidies",
                                  # Alternative to RIMA:
                                  label_question %in% c(  "How would you rate the capacity of the household's income and agricultural production to recover from shocks/perturbations?" ) | name_question %in% c("_2_6_1_3") ~ "Climate_resilience_self_assessed",
                                  label_question %in% c(  "In the last 12 months, what were the most severe shocks faced by the household","What did the household members do to cope with the shocks" ) | name_question %in% c("_4_1_3_1/1") | name_question_recla %in% c("_4_1_3_1", "_4_1_3_1_2") ~ "Shocks_last_12_months",.default=NA)) %>% filter(!is.na(subindicator)) 

# RIMA ABS - Access pillar
temp_kpi_calc <- temp_kpi_calc %>% 
  mutate(subindicator = case_when(grepl("Please select the unit you would like to use", label_question)~"ABS_service_access_unit",
                                 grepl("State the main mode of transport", label_question)~"ABS_service_access_transport",
                                 .default=subindicator)) %>%
  mutate(index = case_when(grepl("AGRICULTURAL/CROPS MARKET",label_question)~"crop_market",
                           grepl("FRESHWATER SOURCE",label_question)~"freshwater",
                           grepl("LIVESTOCK MARKET",label_question)~"livestock_market",
                           grepl("PRIMARY SCHOOL",label_question)~"school",
                           grepl("PUBLIC HOSPITAL",label_question)~"hospital",
                           grepl("PUBLIC TRANSPORT",label_question)~"public_transport",
                           grepl("WELL-MAINTAINED ROAD",label_question)~"road",
                           .default=subindicator))

ABS <- temp_kpi_calc  %>% filter(subindicator %in% c("ABS_service_access", "ABS_service_access_unit", "ABS_service_access_transport"))  %>%  
  dcast(kobo_farmer_id+country+index~subindicator,value.var="name_choice") %>%
  mutate(ABS_service_access = as.numeric(ABS_service_access)) %>%
  mutate(ABS_service_access = ifelse(ABS_service_access %in% c(9999, 999,-9999,-999,5555), NA,ABS_service_access)) %>% 
  # Put all service access times into minutes spent walking
  mutate(ABS_service_access_walking = case_when(ABS_service_access_unit %in% c("km")~(ABS_service_access/5)*60, .default=NA)) %>% # assumes walking speed of 5km/h
  mutate(ABS_service_access_walking = case_when(ABS_service_access_transport %in% c("walking") & ABS_service_access_unit %in% c("minutes")~ABS_service_access, 
    ABS_service_access_transport %in% c("motobike","motorbike", "car")~ABS_service_access*10, # assumes car speed of 50km/h and walking speed of 5 km/h  
                                                ABS_service_access_transport %in% c("cycling")~ABS_service_access*3, # assumes bike speed of 15km/h and walking speed of 5 km/h
                                                ABS_service_access_transport %in% c("horse","donkey")~ABS_service_access*2, # assumes horse speed of 10km/h and walking speed of 5 km/h
                                                .default=ABS_service_access_walking)) %>%
    mutate(ABS_service_access_walking_score = case_when(ABS_service_access_walking < 5 ~ 5,
                           ABS_service_access_walking < 20 ~ 2.5,
                           ABS_service_access_walking >=20 ~ 0,
                           .default=NA)) %>%
  group_by(kobo_farmer_id,country) %>% 
  mutate(ABS_service_access_walking_score = sum(ABS_service_access_walking_score)/7) %>%
  select(kobo_farmer_id,country,ABS_service_access_walking_score) %>% unique() %>%
  full_join(temp_kpi_calc  %>% filter(subindicator %in% c("ABS_service_in_hh"))  %>% 
  mutate(name_choice = as.numeric(name_choice)) %>%
  dcast(kobo_farmer_id~subindicator,value.var="name_choice",sum) %>%
    mutate(ABS_service_in_hh_score = case_when(ABS_service_in_hh >=3~5,
                                               ABS_service_in_hh >=1 & ABS_service_in_hh<3~2.5,
                                               ABS_service_in_hh <1~0,
                                               .default=NA)) %>% select(-ABS_service_in_hh), 
  by=c("kobo_farmer_id")) %>%
  group_by(kobo_farmer_id,country) %>%
  summarise(score_ABS = sum(ABS_service_in_hh_score,ABS_service_access_walking_score)/2)

# RIMA AST - Assets pillar

temp_kpi_calc <- temp_kpi_calc %>% 
  mutate(subindicator = case_when(grepl("Other asset (please specify)", label_question) | name_question == "_4_1_4_13" ~"ABS_assets_other",.default=subindicator))

AST <- temp_kpi_calc  %>% filter(subindicator %in% c("AST_assets")) %>%
  mutate(score = as.numeric(name_choice)) %>%
  mutate(score = ifelse(is.na(score) | score == 0,0,1)) %>%
  dcast(kobo_farmer_id+country~subindicator,value.var="score",sum) %>%
  mutate(score_AST = case_when(AST_assets >=5~5,
                                      AST_assets >=2 & AST_assets <5 ~ 2.5,
                                      AST_assets <2 ~ 0, .default=NA)) %>% select(-AST_assets)
  
# RIMA SSN - Social safety nets pillar

SSN <- temp_kpi_calc  %>% filter(subindicator %in% c("SSN_school_meals")) %>%
    mutate(name_choice = as.numeric(name_choice)) %>%
  dcast(kobo_farmer_id+country~subindicator,value.var="name_choice",mean) %>%
  rename(SSN_school_meals_score = SSN_school_meals) %>%
  full_join(temp_kpi_calc  %>% filter(subindicator %in% c("SSN_hh_support")) %>%
  mutate(name_choice = ifelse(name_choice %in% c("Church","church"),"1",name_choice)) %>%
  #sort(unique(SSN$name_choice)) #sort(unique(SSN$label_question))
# "I don't know" and responses to "Other" are recoded as NA, which produces a warning - this can be ignored
  mutate(name_choice = as.numeric(name_choice)) %>%
  dcast(kobo_farmer_id+country~subindicator,value.var="name_choice",sum) %>%
  mutate(SSN_hh_support_score = case_when(SSN_hh_support >=3~5,
                                      SSN_hh_support >=1 & SSN_hh_support <3 ~ 2.5,
                                      SSN_hh_support <1 ~ 0, .default=0)) %>% select(-SSN_hh_support),
  by=c("kobo_farmer_id","country")) %>%
  group_by(kobo_farmer_id,country) %>%
  summarise(score_SSN = sum(SSN_hh_support_score,SSN_school_meals_score, na.rm=TRUE)/2)

# RIMA AC - Adaptive capacity pillar

AC <- temp_kpi_calc  %>% filter(subindicator %in% c("AC_literacy")) %>%
  mutate(name_choice = ifelse(name_choice %in% c("777","999","5555","9999","-999","-9999"),0,name_choice)) %>%
  mutate(AC_literacy_score = case_when(name_choice %in% c("3")| label_choice %in% c("Can read and write") ~ 5,
                                       name_choice %in% c("1","2")| label_choice %in% c("Can read only", "Can write only") ~ 2.5, 
                                        name_choice %in% c("0","777","999","5555","9999")| label_choice %in% c("Cannot read or write", "Prefer not to say") ~ 0,.default=NA)) %>%
  select(kobo_farmer_id, country, AC_literacy_score) %>% 
  full_join(
    temp_kpi_calc  %>% filter(subindicator %in% c("AC_highest_school_hh_working_age")) %>%
  mutate(AC_highest_school_score = case_when(label_choice %in% c("Secondary","Seconday", "Higher") ~ 5,
                                       label_choice %in% c("Primary") ~ 2.5, 
                                       label_choice %in% c("None") ~ 0,.default=NA)) %>%
  group_by(kobo_farmer_id, country) %>%
  summarise(AC_highest_school_score = mean(AC_highest_school_score)),
  by=c("kobo_farmer_id","country")) %>%
  full_join(
    temp_kpi_calc  %>% filter(subindicator %in% c("AC_training_hh")) %>%
  mutate(name_choice= as.numeric(name_choice)) %>%
  dcast(kobo_farmer_id+country~subindicator,value.var="name_choice",sum) %>%
  mutate(AC_training_score = ifelse(AC_training_hh >=1,5,0)),
  by=c("kobo_farmer_id","country")) %>%
  full_join(
    temp_kpi_calc  %>% filter(subindicator %in% c("AC_income_sources")) %>%
  dcast(kobo_farmer_id+country~subindicator,value.var="name_choice",length) %>%
  mutate(AC_income_sources_score = case_when(AC_income_sources>=3 ~ 5,
                                             AC_income_sources>1 & AC_income_sources<3~ 2.5,
                                             .default=0)) %>%
    select(-AC_income_sources),
  by=c("kobo_farmer_id","country")) %>%
  full_join(temp_kpi_calc  %>% filter(subindicator %in% c("AC_income_on_food")) %>%
  mutate(AC_income_on_food_scores = case_when(name_choice == "1_25"~5,
                                              name_choice == "26_50"~3.33,
                                              name_choice == "51_75"~1.66,
                                              name_choice == "76_100"~0,
                                              .default=NA)) %>%
  select(kobo_farmer_id,country,AC_income_on_food_scores),
    by=c("kobo_farmer_id","country")) %>%
  full_join(
    temp_kpi_calc  %>% filter(subindicator %in% c("AC_access_to_credit")) %>%
  mutate(AC_access_to_credit_score = case_when(name_choice %in% c("2") | label_choice %in% c("Yes, we needed credit and were able to obtain it.")~5,
                                               name_choice %in% c("1","0" ) | label_choice %in% c("No, we did not need credit during that period.", "Yes, we needed credit but could not obtain it.")~0,
                                                name_choice %in% c("3") | label_choice %in% c("Don't know / Not sure")~NA,
                                               .default=NA)) %>%
  select(kobo_farmer_id,country,AC_access_to_credit_score),
    by=c("kobo_farmer_id","country")) %>%
  full_join(
    temp_kpi_calc  %>% filter(subindicator %in% c("AC_credit_repayments")) %>%
   mutate(AC_credit_repayments_score = case_when(name_choice %in% c("4") | label_choice %in% c("We are currently able to meet our loan repayments and confident that we can meet our future repayments.")~5,
                                                 name_choice %in% c("3") | label_choice %in% c("We are currently able to meet our loan repayments, but uncertain about meeting future repayments.")~3.33,
                                                 name_choice %in% c("2") | label_choice %in% c("We are currently not able to meet our loan repayments, but confident about meeting future repayments.")~1.66,
                                                 name_choice %in% c("1") | label_choice %in% c("We are currently not able to meet our loan repayments and uncertain about meeting future repayments.")~0, .default=NA)) %>%
   select(kobo_farmer_id,country, AC_credit_repayments_score),
    by=c("kobo_farmer_id","country")) %>%
  full_join(
    temp_kpi_calc  %>% filter(subindicator %in% c("AC_ag_insurance") & module=="performance") %>%
  mutate(AC_ag_insurance_score = case_when(name_choice %in% c("1","2") | label_choice %in% c("Yes, fully covered", "Yes, partially covered")~5,
                                           name_choice %in% c("0") | label_choice %in% c("No")~0,
                                           .default=NA)) %>%
   select(kobo_farmer_id,country, AC_ag_insurance_score),
    by=c("kobo_farmer_id","country")) %>%
  full_join(
    temp_kpi_calc  %>% filter(subindicator %in% c("AC_ag_subsidies")) %>%
  filter(name_question %in% c("_4_1_1_7")) %>%
  mutate(AC_ag_subsidies_score = case_when(name_choice %in% c("0")| label_choice %in% c("No") ~0, 
                                           name_choice %in% c("1")| label_choice %in% c("Yes") ~5, 
                                           .default=NA)) %>%
    select(kobo_farmer_id,country, AC_ag_subsidies_score),
  by=c("kobo_farmer_id","country"))   %>%
  group_by(kobo_farmer_id,country) %>%
  summarise(score_AC = sum(AC_literacy_score,AC_highest_school_score,AC_training_score, AC_income_sources_score, AC_income_on_food_scores, AC_access_to_credit_score, AC_credit_repayments_score, AC_ag_insurance_score, AC_ag_subsidies_score, na.rm=TRUE)/10)

# RIMA score
temp_kpi_calc1 <- ABS %>% left_join(AST) %>% left_join(SSN) %>% left_join(AC) %>%
    mutate(score = sum(score_ABS, score_AST, score_SSN, score_AC,na.rm=TRUE)) %>% 
  #mutate(score_sum = sum(score_ABS, score_AST, score_SSN, score_AC,na.rm=TRUE),#score_mean = mean(score_ABS, score_AST, score_SSN, score_AC,na.rm=TRUE))
  select(kobo_farmer_id, country, score) %>%
    mutate(indicator = "kpi14a_climate_resilience",
         subindicator = "Climate_resilience_RIMA",
         subindicator_label = "Climate resilience score from 0 (no resilience) to 20 (high resilience), based on assets, access to services, support networks, and adaptive capacity",
         indicator_order = 14.1)

# Shocks_last_12_months
temp_kpi_calc2 <- temp_kpi_calc %>% 
  filter(subindicator %in% c("Climate_resilience_self_assessed")) %>%
  mutate(score = as.numeric(name_choice)) %>%
    select(kobo_farmer_id, country, score) %>%
    mutate(indicator = "kpi14b_climate_resilience",
         subindicator = "Climate_resilience_shock_recovery",
         subindicator_label = "Climate resilience score from 1 (no capacity to recover) to 5 (full recovery) in terms of income and production recovery after shocks or perturbations",
         indicator_order = 14.2)
  
#temp_kpi_calc2 %>% select(subindicator,name_choice,label_choice) %>% unique()

kpi_scores <- kpi_scores %>% full_join(temp_kpi_calc1, keep=NULL) %>% full_join(temp_kpi_calc2, keep=NULL) %>%
  mutate(module = ifelse(indicator %in% c("kpi14a_climate_resilience","kpi14b_climate_resilience"), "performance kpi",module)) %>%
  mutate(theme = ifelse(indicator %in% c("kpi14a_climate_resilience","kpi14b_climate_resilience"), "economic",theme)) 

kpi_histogram(kpi_scores,"kpi14a_climate_resilience")
kpi_histogram(kpi_scores,"kpi14b_climate_resilience")
#kpi_all_boxplot(kpi_scores)

### Performance KPI15 diet quality ####
#sort(unique(d$indicator))
#temp <- d %>% filter(indicator =="nutrition")
#sort(unique(temp$label_question))

# Calculate food group diversity scores
temp_kpi_calc <- d %>% filter(indicator == "nutrition") %>%
  mutate(food_group = case_when(name_question %in% c("_3_1_3_1_1", "_3_1_3_1_2","_3_1_3_1_3")~"grains, roots, tubers",
                                # pulses
                                name_question %in% c("_3_1_3_1_4")~"pulses",
                                name_question %in% c("_3_1_3_1_21")~"nuts and seeds",
                                name_question %in% c("_3_1_3_1_14", "_3_1_3_1_15","_3_1_3_1_25")~"dairy",
                                name_question %in% c("_3_1_3_1_16", "_3_1_3_1_17","_3_1_3_1_18","_3_1_3_1_19", "_3_1_3_1_20")~"meat, poultry, fish",
                                name_question %in% c("_3_1_3_1_13") ~ "eggs",
                                name_question %in% c("_3_1_3_1_6")~"dark leafy vegetables",
                                name_question %in% c("_3_1_3_1_5","_3_1_3_1_8")~"other vit-A rich fruits and vegetables",
                                name_question %in% c("_3_1_3_1_7")~"other vegetables",
                                name_question %in% c("_3_1_3_1_9","_3_1_3_1_10") ~ "other fruits",.default="other FG"))


temp_kpi_calc <- temp_kpi_calc %>%
  dcast(kobo_farmer_id+country+food_group~label_choice,value.var="name_choice",fun=length) %>%  mutate(score_fgds = ifelse(Yes>0 & !(food_group %in% c("other FG")),1,0)) %>%
    group_by(kobo_farmer_id,country) %>%
    summarise(score = sum(score_fgds,na.rm=TRUE)) %>%
  mutate(indicator = "kpi15_diet_diversity",
         subindicator = "FGDS_food_group_diversity_score",
         subindicator_label = "Semi-continuous score of food groups consumed in individual diets from 0 (no diversity) to 10 (high diversity)",
         indicator_order = 15)

kpi_scores <- kpi_scores %>% full_join(temp_kpi_calc, keep=NULL) %>%
  mutate(module = ifelse(indicator %in% c("kpi15_diet_diversity"),"performance kpi",module)) %>%
  mutate(theme = ifelse(indicator %in% c("kpi15_diet_diversity"),"social",theme)) 

kpi_histogram(kpi_scores,"kpi15_diet_diversity")
#kpi_all_boxplot(kpi_scores)

### Performance KPI16 farmer agency ####
#sort(unique(d$indicator))
#temp <- d %>% filter(indicator =="farmer_agency")
#sort(unique(temp$label_question))

d <- d %>% 
  # household agency
    mutate(subindicator = ifelse(label_question ==  "On which step of the ladder would you position the majority of women in your household today?"   ,"agency_hh_f",subindicator)) %>%
  mutate(subindicator = ifelse(label_question ==  "On which step of the ladder would you position the majority of men in your household today?"    ,"agency_hh_m",subindicator)) 
  
  # Put into wide format to align associated data
temp_kpi_calc <- d %>% filter(subindicator %in% c("agency_hh_f","agency_hh_m")) %>%
  dcast(kobo_farmer_id+country+indicator ~subindicator,value.var="name_choice") 

# Calculate indicators of interest
temp_kpi_calc <- temp_kpi_calc %>%
    mutate_at(c("agency_hh_f","agency_hh_m"), ~as.numeric(.)) %>%
  group_by(kobo_farmer_id, country) %>%
  summarise(score = mean(c(agency_hh_f,agency_hh_m),na.rm=T)) %>%
  mutate(indicator = "kpi16_farmer_agency",
         indicator_order = 16,
         subindicator = "agency_hh",
         subindicator_label = "Perceived household agency to make decisions from 1 (no power or freedom) to 5 (total power and freedom)")

kpi_scores <- kpi_scores %>% full_join(temp_kpi_calc, keep=NULL) %>%
  mutate(module = ifelse(indicator %in% c("kpi16_farmer_agency"),"performance kpi",module))  %>%
  mutate(theme = ifelse(indicator %in% c("kpi16_farmer_agency"),"social",theme)) 

kpi_histogram(kpi_scores,"kpi16_farmer_agency")
#kpi_all_boxplot(kpi_scores)

#### Performance KPI17a land tenure security and KPI17b land owned as share of total used ###
#sort(unique(d$indicator))
#temp <- d %>% filter(indicator =="land_tenure_security")
#sort(unique(temp$label_question))

d <- d %>% 
  # total land
  mutate(subindicator = ifelse(label_question ==  "What is the total area in hectares (or acres) of land (agricultural or not) that your household: Currently OWNS:"    ,"land_owned_hh",subindicator)) %>%
  mutate(subindicator = ifelse(label_question ==  "What is the total area in hectares (or acres) of land (agricultural or not) that your household: Currently LEASES from another person:" ,"land_leased_hh",subindicator)) %>% 
  mutate(subindicator = ifelse(label_question ==  "What is the total area in hectares (or acres) of land (agricultural or not) that your household: Currently HOLDS USE RIGHTS, either alone or jointly with someone else:" ,"land_rights_hh",subindicator)) %>%
  
  # land owned
  mutate(subindicator = ifelse(label_question == "From the ${_1_4_1_1_1} ${_1_4_1_1_calculate} of land that your household OWNS, please specify how much is owned by: A FEMALE member/members:" ,"land_owned_f",subindicator)) %>%
  mutate(subindicator = ifelse(label_question=="From the ${_1_4_1_1_1} ${_1_4_1_1_calculate} of land that your household OWNS, please specify how much is owned by: A MALE member/members:" ,"land_owned_m",subindicator)) %>%
  
  # land leased
  mutate(subindicator = ifelse(label_question=="From the ${_1_4_1_1_2} ${_1_4_1_1_calculate} of land that your household LEASES from another person, please specify how much is rented by: A FEMALE member/members:" ,"land_leased_f",subindicator)) %>%
  mutate(subindicator = ifelse(label_question=="From the ${_1_4_1_1_2} ${_1_4_1_1_calculate} of land that your household LEASES from another person, please specify how much is rented by: A MALE member/members:"  ,"land_leased_m",subindicator)) %>%
  
    # land use rights
  mutate(subindicator = ifelse(label_question=="From the ${_1_4_1_1_3} ${_1_4_1_1_calculate} of land (agricultural or not) that your household HOLDS USE RIGHTS, either alone or jointly with someone else, please specify how much is held by: A FEMALE member/members:" ,"land_rights_f",subindicator)) %>%
  mutate(subindicator = ifelse(label_question== "From the ${_1_4_1_1_3} ${_1_4_1_1_calculate} of land (agricultural or not) that your household HOLDS USE RIGHTS, either alone or jointly with someone else, please specify how much is held by: A MALE member/members:", "land_rights_m",subindicator)) %>%
  
  # land area that is vulnerable
    mutate(subindicator = ifelse(label_question=="What is the total area of your land that could be affected?"  ,"land_vulnerable_area",subindicator)) %>%
  mutate(subindicator = ifelse(label_question=="Do you perceive that you could involuntarily lose ownership or use rights to any of the land (agricultural or not) you currently own or hold use rights to in the next 5 years?" ,"land_security_perceived",subindicator)) %>%
  
  # For perceived loss of land access, make sure that name_choice values are in format 5 = no risk of loss, 1 = high risk of loss
  mutate(name_choice = ifelse(subindicator=="land_security_perceived" & label_choice=="Extremely likely",1,
                ifelse(subindicator=="land_security_perceived" & label_choice == "Very likely",2,
                       ifelse(subindicator=="land_security_perceived" & label_choice == "Moderately likely",3,
                              ifelse(subindicator=="land_security_perceived" & label_choice == "Slightly likely" ,4,
                                     ifelse(subindicator=="land_security_perceived" & label_choice == "Not at all" ,5,name_choice)))))) 

# Put into wide format to align associated data
temp_kpi_calc <- d %>% filter(indicator =="land_tenure_security") %>%
  dcast(kobo_farmer_id+country+indicator ~subindicator,value.var="name_choice") 

# Calculate indicators of interest

temp_kpi_calc <- temp_kpi_calc  %>%
  mutate(land_vulnerable_area = ifelse(country=="peru",NA,land_vulnerable_area)) %>%
    mutate_at(c("land_leased_f" , "land_leased_hh"    ,   "land_leased_m" ,       "land_owned_f"     ,    "land_owned_hh"   ,  "land_owned_m"  ,       "land_rights_f",        "land_rights_hh" ,      "land_rights_m" ,  "land_vulnerable_area","land_security_perceived"), ~ifelse(is.na(.),0,as.numeric(.))) %>%
  mutate(land_vulnerable_share = land_vulnerable_area/(land_owned_hh+land_leased_hh + land_rights_hh)*100) %>%
  mutate(land_vulnerable_share = ifelse(land_vulnerable_share>100,100,land_vulnerable_share)) %>%
  mutate(land_not_vulnerable_share = 100 - land_vulnerable_share) %>%
  mutate(land_owned_share = land_owned_hh/(land_owned_hh+land_leased_hh + land_rights_hh)*100) %>%
   mutate(land_owned_share = ifelse(land_owned_share>100,100,land_owned_share)) %>%
  mutate(land_security_perceived_weighted = ifelse(land_vulnerable_share>0 & !is.na(land_vulnerable_share),(land_security_perceived * (land_vulnerable_share/100))+(5*(land_not_vulnerable_share/100)),land_security_perceived)) %>%
  # cap the minimum to a score of 1
  mutate(land_security_perceived_weighted = ifelse(land_security_perceived_weighted<1,1,land_security_perceived_weighted))

temp_kpi_calc <- temp_kpi_calc %>% 
  melt(id.vars=c("kobo_farmer_id","country","indicator"), measure.vars=c("land_owned_share","land_security_perceived","land_security_perceived_weighted"),variable.name="subindicator",value.name="score") 

# Add this back into the main dataset

temp_kpi_calc <- temp_kpi_calc %>%
  filter(!(subindicator=="land_security_perceived")) %>%
  select(kobo_farmer_id,country,indicator,subindicator,score) %>%
  mutate(indicator = ifelse(subindicator == "land_security_perceived_weighted", "kpi17a_land_tenure", indicator)) %>%
  mutate(indicator = ifelse(subindicator=="land_owned_share","kpi17b_land_tenure",indicator)) 
    
kpi_scores <- kpi_scores %>% full_join(temp_kpi_calc, by = c("kobo_farmer_id", "country", "indicator", "subindicator", "score"), keep=NULL) %>%
  mutate(subindicator_label = ifelse(indicator=="kpi17a_land_tenure","Perceived land tenure security from 1 = (Extremely likely to lose access to all land) to 5 (Not at all likely to lose access to any land)",subindicator_label)) %>%
  mutate(indicator_order = ifelse(indicator =="kpi17a_land_tenure",17.1,indicator_order)) %>%
  mutate(subindicator_label = ifelse(indicator=="kpi17b_land_tenure","Share of household land that is owned (%)",subindicator_label)) %>%
  mutate(indicator_order = ifelse(indicator =="kpi17b_land_tenure",17.2,indicator_order)) %>%
  mutate(module = ifelse(indicator %in%  c("kpi17a_land_tenure", "kpi17b_land_tenure"), "performance kpi",module)) %>%
  mutate(theme = ifelse(indicator %in% c("kpi17a_land_tenure","kpi17b_land_tenure"),"social",theme)) 

kpi_histogram(kpi_scores,"kpi17a_land_tenure")
kpi_histogram(kpi_scores,"kpi17b_land_tenure")
#kpi_all_boxplot(kpi_scores)
  
### Performance KPI18 human wellbeing ####
#sort(unique(d$indicator))
#temp <- d %>% filter(indicator =="wellbeing")
#sort(unique(temp$subindicator))
#sort(unique(temp$label_question))
#sort(unique(temp$label_choice))

d <- d %>% 
  mutate(subindicator = case_when(label_question == "How satisfied are you with feeling part of your community?" ~"satisfaction_community",
                                  label_question == "How satisfied are you with how safe you feel?" ~ "satisfaction_safety",
                                  label_question =="How satisfied are you with the amount of time you have to do the things that you like doing?"~"satisfaction_time",
                                  label_question == "How satisfied are you with the quality of your local environment?"~"satisfaction_environment",
                                  label_question == "How satisfied are you with what you are achieving in life?"~"satisfaction_achievements",
                                  label_question=="How satisfied are you with your economic security?"~ "satisfaction_economic",
                                  label_question== "How satisfied are you with your health?"~"satisfaction_health",
                                  label_question=="How satisfied are you with your nutritional security?"~"satisfaction_nutritional",
                                  label_question=="How satisfied are you with your occupation?" ~"satisfaction_occupation",
                                  label_question=="How satisfied are you with your personal relationships?" ~"satisfaction_relationships",
                                  label_question=="How satisfied are you with your standard of living?"~"satisfaction_livingstandard",
                                  label_question=="Thinking about your own life and personal circumstances, how satisfied are you with your life as a whole?"~"satisfaction_overall", .default=subindicator)) %>%
  mutate(score = case_when(indicator=="wellbeing" & label_choice=="Completely satisfied."~5,
                indicator=="wellbeing" & label_choice == "Somewhat satisfied."~4,
                indicator=="wellbeing" & label_choice == "Neutral"~3,
                indicator=="wellbeing" & label_choice == "Somewhat dissatisfied."~2,
                indicator=="wellbeing" & label_choice == "Completely dissatisfied."~1,.default=score)) 

temp_kpi_calc <- d %>% filter(indicator=="wellbeing") %>%
  mutate(score = as.numeric(score)) %>%
  group_by(kobo_farmer_id, country, indicator) %>%
  summarise(score = median(score,na.rm=TRUE)) %>% ungroup() %>%
  mutate(indicator = "kpi18_human_wellbeing",
           subindicator = "wellbeing_average")

kpi_scores <- kpi_scores %>% full_join(temp_kpi_calc, by = c("kobo_farmer_id", "country", "indicator", "subindicator", "score"), keep=NULL) %>%
  mutate(subindicator_label = ifelse(indicator=="kpi18_human_wellbeing","Perceived life satisfaction from 1 (Completely dissatisfied) to 5 (Completely satisfied)",subindicator_label)) %>%
  mutate(indicator_order = ifelse(indicator =="kpi18_human_wellbeing",18,indicator_order)) %>%
  mutate(module = ifelse(indicator == "kpi18_human_wellbeing","performance kpi",module)) %>%
    mutate(theme = ifelse(indicator %in% c("kpi18_human_wellbeing"),"social",theme)) 

kpi_histogram(kpi_scores,"kpi18_human_wellbeing")

kpi_all_boxplot(kpi_scores %>% filter(theme %in% c("agricultural","economic")))
ggsave(paste0(global.data.path,"figures/kpi boxplots agr-eco ",country,".tif"),width=12,height=12,units="in")

kpi_all_boxplot(kpi_scores %>% filter(theme %in% c("environmental","social")))
ggsave(paste0(global.data.path,"figures/kpi boxplots env-soc ",country,".tif"),width=12,height=12,units="in")

```

## Transfrom KPIs to unform 1 to 100 scale

This section puts all performance indicators on a consistent scale, from 0 (worse) to 100 (better). It also adds an 'indicator group' column representing the 18 performance theme names, separate from the list of indicators used to measure each theme, to be consistent with our framework figure

```{r KPI scaling, include=TRUE, echo=FALSE}

#country <- "burkina"
#kpi_scores <- read.csv(paste0(bfa.data.path,"bfa_kpi_scores_20241209.csv"),header=TRUE) %>% select(-score_scaled)
#country <- "india"
#country <- "laos"
#kpi_scores <- read.csv(paste0(lao.data.path,"lao_kpi_scores_20241209.csv"),header=TRUE) %>% select(-score_scaled)
#country <- "kenya"
#kpi_scores <- read.csv(paste0(ken.data.path,"ken_kpi_scores_20241211.csv"),header=TRUE) %>% select(-score_scaled)
#country <- "peru"
#kpi_scores <- read.csv(paste0(per.data.path,"per_kpi_scores_20241211.csv"),header=TRUE) %>% select(-score_scaled)
#country <- "senegal" 
#kpi_scores <- read.csv(paste0(sen.data.path,"sen_kpi_scores_20241211.csv"),header=TRUE) %>% select(-score_scaled)
#country <- "tunisia"
#kpi_scores <- read.csv(paste0(tun.data.path,"tun_kpi_scores_20241211.csv"),header=TRUE) %>% select(-score_scaled)
#country <- "zimbabwe"
#kpi_scores <- read.csv(paste0(zwe.data.path,"zwe_kpi_scores_20241211.csv"),header=TRUE) %>% select(-score_scaled)

# Make function to transform KPI scores from 0 to 100 scale
indicators_scaled <- data.frame(kobo_farmer_id=as.numeric(NA),
                      theme=as.character(NA),
                      ind_group=as.character(NA),
                      kpi_label_short=as.character(NA),
                      indicator=as.character(NA),
                      indicator_order=as.numeric(NA),
                      subindicator = as.character(NA), 
                      subindicator_label = as.character(NA),
                      score=as.numeric(NA),
                      score_scaled=as.numeric(NA))
indicators_scaled <- indicators_scaled[-1,]

indicator_scaling <- function(data, ind, method, min=NA,max=NA,ind_group,kpi_label_short){
  data_subset <- data %>% filter(indicator %in% c(ind))
  # no scaling needed (e.g. scores in %)
  if(method =="none"){
  data_subset$score_scaled <- as.numeric(data_subset$score)
  }
  # scaling based on min and max values recorded in the survey
  if(method =="data_driven"){
  ind_min <- min(as.numeric(data_subset$score),na.rm=TRUE)
  ind_max <- max(as.numeric(data_subset$score),na.rm=TRUE)
  data_subset$score_scaled <- (data_subset$score - ind_min)/(ind_max - ind_min)*100
  }
  # inverse scaling based on min and max values recorded in the survey
  if(method =="data_driven_inverse"){
  ind_min <- min(as.numeric(data_subset$score),na.rm=TRUE)
  ind_max <- max(as.numeric(data_subset$score),na.rm=TRUE)
  data_subset$score_scaled <- 100 - ((data_subset$score - ind_min)/(ind_max - ind_min)*100)
  }
  # scaling based on pre-defined min and max values 
  if(method =="set"){
  ind_min <- as.numeric(min)
  ind_max <- as.numeric(max)
  data_subset <- data_subset %>% mutate(score = ifelse(score <= ind_min,ind_min,ifelse(score>=ind_max, ind_max, score)))
  data_subset$score_scaled <- (data_subset$score - ind_min)/(ind_max - ind_min)*100
  }
  data_subset <- data_subset %>% 
    mutate(ind_group = ind_group, kpi_label_short=kpi_label_short) %>%
    select(c("kobo_farmer_id","theme","ind_group","kpi_label_short", "indicator","indicator_order","subindicator","subindicator_label", "score", "score_scaled"))
  indicators_scaled <- indicators_scaled %>% rbind(data_subset)
  assign("indicators_scaled",indicators_scaled,envir = globalenv())
  rm(data, ind, method, min,max)
}

print(kpi_scores %>% select(indicator, subindicator_label) %>% unique())#, n=30)

indicator_scaling(kpi_scores, ind="kpi1_crop_health",method="none", ind_group="Crop health",kpi_label_short="Crop health (% loss)")
indicator_scaling(kpi_scores, ind="kpi1b_crop_health_fieldwork",method="set", min=1,max=5, ind_group="Crop health",kpi_label_short="Crop health (SOCLA)")
indicator_scaling(kpi_scores, ind="kpi2_animal_health", method="set", min=1,max=5, ind_group="Animal health",kpi_label_short="Animal health (qual)")
indicator_scaling(kpi_scores, ind="kpi3_soil_health",method="set",min=1,max=5, ind_group="Soil health",kpi_label_short="Soil health (qual)")
indicator_scaling(kpi_scores, ind="kpi4_nutrient_use",method="set",min=0.5,max=2, ind_group="Nutrient use",kpi_label_short="Nutrient use (versus average)")
indicator_scaling(kpi_scores, ind="kpi5a_animal_diversity", method="set",min=1,max=5, ind_group="Biodiversity",kpi_label_short="Animal diversity (qual)")
indicator_scaling(kpi_scores, ind="kpi5b_tree_diversity", method="set",min=1,max=5, ind_group="Biodiversity",kpi_label_short="Tree diversity (qual)")
indicator_scaling(kpi_scores, ind="kpi6a_abd_crop_richness_index", method="none", ind_group="Agrobiodiversity",kpi_label_short="Crop richness (versus max)") 
indicator_scaling(kpi_scores, ind="kpi6b_abd_variety_diversity", method="set" ,min=1,max=5, ind_group="Agrobiodiversity",kpi_label_short="Varietal diversity (qual)") 
indicator_scaling(kpi_scores, ind="kpi7_landscape_complexity", method="set" ,min=1,max=5, ind_group="Landscape complexity",kpi_label_short="Landscape complexity (%)")
indicator_scaling(kpi_scores, ind="kpi8_climate_mitigation", method="set" ,min=1,max=5, ind_group="Climate mitigation",kpi_label_short="Climate mitigation (qual)") 
indicator_scaling(kpi_scores, ind="kpi9_avoided_ag_water_stress", method="none", ind_group="Water use",kpi_label_short="Avoided ag water stress (% months)")
indicator_scaling(kpi_scores, ind="kpi9b_avoided_irrigation_water_stress", method="none", ind_group="Water use",kpi_label_short="Avoided irrigation water stress (% months)")
indicator_scaling(kpi_scores, ind="kpi10_energy_use", method="set" ,min=1,max=5, ind_group="Energy use",kpi_label_short= "Energy sustainability (qual)")
indicator_scaling(kpi_scores, ind="kpi11_hh_income_v_mean", method="set", min=0.5, max=2, ind_group="Income",kpi_label_short= "HH income (versus average)")
indicator_scaling(kpi_scores, ind="kpi11b_hh_income_stability",method="set",min=1,max=5, ind_group="Income",kpi_label_short="HH income stability (qual)") 
indicator_scaling(kpi_scores, ind="kpi11c_hh_income_v_expenditures", method="set",min=0,max=1, ind_group="Income",kpi_label_short="HH income versus expenditures (binary)") 
indicator_scaling(kpi_scores, ind="kpi11d_hh_income_sufficiency",method="set",min=1,max=5, ind_group="Income",kpi_label_short="HH income sufficiency (qual)")  
indicator_scaling(kpi_scores, ind="kpi12_yield_gap", method="set",min=0,max=99, ind_group="Agricultural productivity",kpi_label_short="Yield gap (%)")  
indicator_scaling(kpi_scores, ind="kpi13a_labour_input", method="data_driven_inverse", ind_group="Labour",kpi_label_short="Reduced labour input (hrs/yr/ha)") # used inverse so higher values are better, i.e. less labour per ha. Need to get min and max across all countries to allow for better comparisons.
indicator_scaling(kpi_scores, ind="kpi13b_labour_productivity", method="data_driven", ind_group="Labour",kpi_label_short="Labour productivity (USD/hrs/yr)") # Need to set min and max across all countries to allow for better comparisons. 
indicator_scaling(kpi_scores, ind="kpi14a_climate_resilience", method="set",min=0,max=20, ind_group="Climate resilience",kpi_label_short="Climate resilience (RIMA)")
indicator_scaling(kpi_scores, ind="kpi14b_climate_resilience",  method="set",min=1,max=5, ind_group="Climate resilience",kpi_label_short="Recovery after shocks (qual)")
indicator_scaling(kpi_scores, ind="kpi15_diet_diversity", method="set",min=0,max=10, ind_group="Diet diversity",kpi_label_short= "Diet diversity (MFGD)")
indicator_scaling(kpi_scores, ind="kpi16_farmer_agency", method="set",min=1,max=5, ind_group="Farmer agency",kpi_label_short="Farmer agency (qual)")
indicator_scaling(kpi_scores, ind="kpi17a_land_tenure", method="set",min=1,max=5, ind_group="Land tenure",kpi_label_short="Land security (qual)")
indicator_scaling(kpi_scores, ind="kpi17b_land_tenure", method="none", ind_group="Land tenure",kpi_label_short="Land security (% owned)")
indicator_scaling(kpi_scores, ind="kpi18_human_wellbeing", method="set",min=1, max=5, ind_group="Human wellbeing",kpi_label_short="Human wellbeing (qual)")

# Add scaled scores to main dataset
kpi_scores_final <- kpi_scores %>% left_join(indicators_scaled %>% select(-score), relationship="many-to-many")  %>%
  mutate(kpi_order = gsub("(.+?)(\\_.*)","\\1", indicator)) %>%
  mutate(kpi_label= paste0(gsub("(.+?)(\\_.*)","\\1", indicator),": ",subindicator_label)) %>%
  mutate(kpi_label = factor(kpi_label, levels=unique(kpi_label[order(indicator_order)]))) %>%
  select(c("kobo_farmer_id","country","module", "theme","ind_group", "indicator","indicator_order","kpi_order", "kpi_label","kpi_label_short", "subindicator","subindicator_label", "score", "score_scaled")) %>% 
  filter(!is.na(module)) %>%
  # add in missing ind_group and kpi_label_short names  
  mutate(ind_group = case_when(indicator =="kpi7_landscape_complexity"~"Landscape complexity",
                                     indicator =="kpi8_climate_mitigation"~"Climate mitigation", .default=ind_group)) %>%  
  mutate(kpi_label_short = case_when(indicator =="kpi7_landscape_complexity"~"Landscape complexity (qual)",
                                     indicator =="kpi8_climate_mitigation"~"Climate mitigation (qual)", .default=kpi_label_short))

# Save data for re-use in next script
export_kpi_scores <- function(country){
  if(country == "burkina"){
    write.csv(d,paste0(bfa.data.path,"bfa_data.csv"),row.names=FALSE)
    write.csv(kpi_scores_final,paste0(bfa.data.path,"bfa_kpi_scores_",format(Sys.Date(), "%Y%m%d"),".csv"),row.names=FALSE) }
  if(country=="india"){
    write.csv(d,paste0(ind.data.path,"ind_data.csv"),row.names=FALSE)
    write.csv(kpi_scores_final,paste0(ind.data.path,"ind_kpi_scores_",format(Sys.Date(), "%Y%m%d"),".csv"),row.names=FALSE)}
  if(country=="laos"){
    write.csv(d,paste0(lao.data.path,"lao_data.csv"),row.names=FALSE)
    write.csv(kpi_scores_final,paste0(lao.data.path,"lao_kpi_scores_",format(Sys.Date(), "%Y%m%d"),".csv"),row.names=FALSE)}
  if(country=="kenya"){
    write.csv(d,paste0(ken.data.path,"ken_data.csv"),row.names=FALSE)
    write.csv(kpi_scores_final,paste0(ken.data.path,"ken_kpi_scores_",format(Sys.Date(), "%Y%m%d"),".csv"),row.names=FALSE)}
  if(country=="peru"){
    write.csv(d,paste0(per.data.path,"per_data.csv"),row.names=FALSE)
    write.csv(kpi_scores_final,paste0(per.data.path,"per_kpi_scores_",format(Sys.Date(), "%Y%m%d"),".csv"),row.names=FALSE)}
  if(country=="senegal"){
    write.csv(d,paste0(sen.data.path,"sen_data.csv"),row.names=FALSE)
    write.csv(kpi_scores_final,paste0(sen.data.path,"sen_kpi_scores_",format(Sys.Date(), "%Y%m%d"),".csv"),row.names=FALSE)  }
  if(country=="tunisia"){
    write.csv(d,paste0(tun.data.path,"tun_data.csv"),row.names=FALSE)
    write.csv(kpi_scores_final,paste0(tun.data.path,"tun_kpi_scores_",format(Sys.Date(), "%Y%m%d"),".csv"),row.names=FALSE)
  }
  if(country == "zimbabwe"){
    write.csv(d,paste0(zwe.data.path,"zwe_data.csv"),row.names=FALSE)
    write.csv(kpi_scores_final,paste0(zwe.data.path,"zwe_kpi_scores_",format(Sys.Date(), "%Y%m%d"),".csv"),row.names=FALSE)
  }
}

export_kpi_scores(country)

# Gauge plots showing scaled indicator scores
kpi_all_gauge(kpi_scores_final)
ggsave(paste0(global.data.path,"figures/kpi_scaled_gauge_plots_",country,".tif"),width=7,height=12,units="in")

# Bar chart with errorbars with scaled indicator scores
kpi_all_barchart(kpi_scores_final)
ggsave(paste0(global.data.path,"figures/kpi_scaled_barplot_",country,".tif"),width=7,height=5.5,units="in")

```

